### 2020-04-06 paper2_choice of fig.Rmd
prep for final figures

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

# Figures specification
* titled
* cited in numerical order in the text using Arabic numbers. 
* no additional charges for color. 
* submitted as individual files
* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
* Figures may be submitted as multipart panels.
*  *.tif* or .eps 
* final publication size; 1-column width or, if necessary, 1½ column width. The * 2-column width should not be used unless necessary.
* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
* Calibri font sub sans serif Arial
* Multipanel labeled using uppercase 12-point Calibri Bold. 
* minimum text size of 6 points
* bold enough to be easily read after reduction, as should all symbols used in the * figure. Line or bar graphs or flow charts with text should be created in black and * white, not shades of gray, which are difficult to reproduce in even tones. If more * than two sets of data are represented, use of fill patterns or colors (not gray) is * suggested to present the data clearly.
* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for * combination halftones, and 1000 dpi for line art.

```{r pkg}
library(tidyverse)
library(RColorBrewer)
library(readxl)
library(kableExtra)
library(tiff)
library(grid)
```

```{r}

# palette
blues <- brewer.pal(9,"Blues")
greens <- brewer.pal(9,"Greens")
excel_pal <- c("#CEDBE6", "#3494BA", "#58B6C0", "#75BDA7", "#84ACB6", "#2683C6", "#373545")
greys <- gray.colors(6, start = 0, end = 1)

# figure saving settings
units = "in"
fig_w <- 3.2
fig_w_1.5 <- 4.5
fig_h <- 4.5
fig_h_1.5 <- 4.5 * 1.5
dpi <- 300
device <- "tiff"

```

```{r import}
file <- here::here("data", "Meta-Analysis Data Collection.xlsx")

# added a row for column names more useful
# # skipped first two rows of of old col names

dat <- read_excel(file, sheet = "Data")

```

## Other palettes

All colour blind-friendly.

```{r}
display.brewer.all(colorblindFriendly = TRUE)
```
```{r fig.height=.2, fig.width=6}
df <- data.frame(x = 1:6, y = 1)
pal <- viridisLite::viridis(6)
df %>% ggplot(aes(x = factor(x), y = y, fill = factor(x))) +
  geom_col(fill = pal) +
  theme_void()
pal <- viridisLite::viridis(6, option = "A")
df %>% ggplot(aes(x = factor(x), y = y, fill = factor(x))) +
  geom_col(fill = pal) +
  theme_void()
pal <- viridisLite::viridis(6, option = "B")
df %>% ggplot(aes(x = factor(x), y = y, fill = factor(x))) +
  geom_col(fill = pal) +
  theme_void()
pal <- viridisLite::viridis(6, option = "C")
df %>% ggplot(aes(x = factor(x), y = y, fill = factor(x))) +
  geom_col(fill = pal) +
  theme_void()
```

Note: there is a 85th line containing only a note in the `NOTES` variable - presumably it belongs elsewhere and was excluded. The note was "compares different papers on bone marrow MSCs, doesn't say anything about prep of cells"

```{r tidy-data}
# recode country so those with one paper are
# "Other"
dat <- dat %>%
  mutate(Country2 = recode_factor(Country,
                                Brazil = "Brazil",
                                China = "China",
                                Denmark = "Denmark",
                                Egypt = "Egypt",
                                India = "India",
                                Japan = "Japan",
                                Korea = "Korea",
                                Netherlands = "Netherlands",
                                Poland = "Poland",
                                `Rep Korea` = "Rep Korea",
                                Russia = "Russia",
                                Spain = "Spain",
                                Taiwan = "Taiwan",
                                USA = "USA",
                                .default = "Other"))

dat <- dat %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

# test results - there is no "t" in the data file and there are more
# blanks values than t's in draft paper fig 6
dat <- dat %>%
  mutate(test_results = recode_factor(`Test Results?`,
                                       n = "Average value",
                                       s = "Stated as 'standard phenotype'",
                                       o = "Not discussed",
                                       y = "Phenotypic markers reported",
                                       t = "Tests done but not reported"))
dat$test_results <- fct_relevel(dat$test_results,
                              "Phenotypic markers reported", 
                              "Average value",
                              "Tests done but not reported",
                              "Stated as 'standard phenotype'",
                              "Not discussed")

# MOA - recode NS to Not stated
dat <- dat %>%
  mutate(MOA = recode_factor(MOA,
                             NS = "Not stated",
                             paracrine = "Paracrine",
                             immune = "Immune",
                             differentiation = "Differentiation",
                             multi = "Muliple"))

dat$MOA <- fct_relevel(dat$MOA,
                       "Paracrine",
                       "Immune",
                       "Differentiation",
                       "Muliple",
                       "Not stated")

# recode stem/stromal
dat <- dat %>%
  mutate(stem_stromal = recode_factor(`Stem/Stromal`,
                             `multipotent stromal` = "Multipotent Stromal",
                             other = "Other",
                             stem = "Stem",
                             stromal = "Stromal"))

dat$stem_stromal <- fct_relevel(dat$stem_stromal,
                                "Stromal",
                                "Stem",
                                "Multipotent Stromal",
                                "Other")

# Recode O, A and C into the 5 categories that appar 
dat <- dat %>%
  mutate(potency = ifelse(O == "y" &
                            A == "y" &
                            C == "y",
                          "Demonstrated tripotency",
                          ifelse(O == "n" &
                                   A == "n" &
                                   C == "n",
                                 "Not Stated",
                                 ifelse(O == "y" &
                                          A == "y" &
                                          C == "n",
                                        "Demonstrated bipotency (OA)",
                                        ifelse(O == "m"
                                               & A == "m" &
                                                 C == "n",
                                               "Claimed bipotency (OA)",
                                               ifelse(O == "m" &
                                                  A == "m" &
                                                  C == "m",
                                                  "Claimed tripotency", NA))))))

dat$potency <- fct_relevel(dat$potency,
                                "Demonstrated tripotency",
                                "Demonstrated bipotency (OA)",
                                "Claimed tripotency",
                                "Claimed bipotency (OA)",
                                "Not Stated")

######### code for "Data Tab copy v1.csv"
# # column indices for markers
# firstmarker <- which(colnames(dat) == "CD73")
# lastmarker <- which(colnames(dat) == "SSEA.4")
# # vector of marker names
# markers <- names(dat[firstmarker:lastmarker])
# 
# datnum <- dat %>% 
#   select(markers) %>% 
#   mutate_all(as.numeric) 
# 
# # add the non marker columns
# notmarkers <- which(!(colnames(dat) %in% markers))
# datnum <- cbind(dat[notmarkers], datnum)
# 
# 
# dat$Stem.Stromal <- factor(dat$Stem.Stromal)
# dat$Year <- factor(dat$Year)
# datnum$Stem.Stromal <- factor(datnum$Stem.Stromal)
# datnum$Year <- factor(datnum$Year)

```
# Figures
Note: tifs are of high quality than appear in this doc

## Fig 1 - Article search funnel

Funnel plot - could be adapted to include the reviews adjacent and aligned with the articles plot.

> to do: Add the Reviews diagram

```{r data-prep-fig1}
# create data
# short names for proof of method
orig <- data.frame(step_names = c("1.mesenchymal",
                                  "2.article",
                                  "3.cell tissue etc",
                                  "4.clinical etc",
                                  "5.not biotech etc",
                                  "6.exc conf etc"),
                   n = c(65706,
                         47031,
                         7814,
                         5502,
                         2055,
                         1986))

orig$step_names <- fct_relevel(orig$step_names,
                               "mesenchymal",
                               "article",
                               "cell tissue etc",
                               "clinical etc",
                               "not biotech etc",
                               "exc conf etc")

# prep polygons that connect
to_poly_orig <- orig %>%
  arrange(n) %>%
  mutate(
    group = row_number(),
    x1 = 0 + ((1 - n)/2),
    x4 = n + ((1 - n)/2),
    x2 = lag(x1), 
    x3 = lag(x4)) %>%
  mutate(
    x2 = ifelse(is.na(x2), x1, x2),
    x3 = ifelse(is.na(x3), x4, x3)
  ) %>%
  gather(xpoint, x, -step_names,-group, -n) %>%
  arrange(group, xpoint) %>%
  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))

# EXAMPLE
# Create the placement of the stages in the plot,
#  by just adding a 0.5 to each row number

labels <- orig %>%
  arrange(n) %>%
  mutate(y = row_number() + 0.5)

# modify the labels
labels$step_names2 <- c( "EXCLUDE conference proceedings,\nretracted papers",
                         "EXCLUDE CATEGORIES (NOT\nbiotechnology applied microbiology oncology\nhaematology, engineering biomedical)",
                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative medicine)",
                         "REFINE BY CATEGORY\ncell tissue engineering\nand transplantation",
                         "REFINE BY DOCUMENT TYPE\narticle",
                         "mesenchymal stem cells OR\nmesenchymal stromal cells OR\nMSC AND characterisation AND clinical")
```

```{r fig1-blues}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               color = "black") +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = blues)

ggsave("figs/fig_1_Article_search_funnel_blues.tif", 
       plot = article_funnel, 
       device = device,
       width = fig_w, 
       height = 3.0,
       units = units,
       dpi = dpi)
```

```{r}
grid.raster(readTIFF("figs/fig_1_Article_search_funnel_blues.tif"))
```

```{r fig1-excel}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               color = "black") +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = excel_pal)

ggsave("figs/fig_1_Article_search_funnel_excel.tif", 
       plot = article_funnel, 
       device = device,
       width = fig_w, 
       height = 3.0,
       units = units,
       dpi = dpi)
```

```{r}
grid.raster(readTIFF("figs/fig_1_Article_search_funnel_excel.tif"))
```

```{r fig1-greys}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               color = "black") +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = rev(greys))

ggsave("figs/fig_1_Article_search_funnel_greys.tif", 
       plot = article_funnel, 
       device = device,
       width = fig_w, 
       height = 3.0,
       units = units,
       dpi = dpi)
```

```{r}
grid.raster(readTIFF("figs/fig_1_Article_search_funnel_greys.tif"))
```

## Figure 3 Articles by country

```{r country-prep}
summary_country <- dat %>%
  group_by(Country) %>% 
  summarise(n = length(Country))

```

```{r fig3-country-bar-blues}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4],
           colour = "black") +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country_blues.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_3_Article_country_blues.tif"))
```

```{r fig3-country-bar-excel}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = excel_pal[3],
           colour = "black") +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country_excel.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_3_Article_country_excel.tif"))
```

```{r fig3-country-bar-greys}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = "white",
           colour = "black") +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country_greys.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_3_Article_country_greys.tif"))
```

## Figure 4 Articles by Phase

### Six phase version

```{r phase-prep}
summary_phase <- dat %>%
  group_by(Phase) %>% 
  summarise(n = length(Phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))
summary_phase <- summary_phase %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

summary_phase_condensed <- dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

```

```{r fig4-phase-blues}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4], colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 1),
                     limits = c(0, 30),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_blues.tif", 
       plot = phase_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_blues.tif"))
```

```{r fig4-phase-excel}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = excel_pal[3], colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 1),
                     limits = c(0, 30),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_excel.tif", 
       plot = phase_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_excel.tif"))
```

```{r fig4-phase-greys}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = "white", colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 30, 5),
                     minor_breaks = seq(0, 30, 1),
                     limits = c(0, 30),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_greys.tif", 
       plot = phase_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_greys.tif"))
```

### Three phase

```{r fig4-phase-3-blues}
phase_3_bar <- summary_phase_condensed %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4], colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 60, 5),
                     minor_breaks = seq(0, 60, 1),
                     limits = c(0, 60),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_3_blues.tif", 
       plot = phase_3_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_3_blues.tif"))
```

```{r fig4-phase-3-excel}
phase_3_bar <- summary_phase_condensed %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
  geom_bar(stat = "identity", fill = excel_pal[3], colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 60, 5),
                     minor_breaks = seq(0, 60, 1),
                     limits = c(0, 60),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_3_excel.tif", 
       plot = phase_3_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_3_excel.tif"))
```

```{r fig4-phase-3-greys}
phase_3_bar <- summary_phase_condensed %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
  geom_bar(stat = "identity", fill = "white", colour = "black") +
  xlab("") +
  geom_text(aes(y = 10, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 60, 5),
                     minor_breaks = seq(0, 60, 1),
                     limits = c(0, 60),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_3_greys.tif", 
       plot = phase_3_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_4_Article_phase_3_greys.tif"))
```

## Figure 5 Articles by Source-Year

Done with bars side-by-side or stacked.

### besides

```{r source_year_prep}
summary_tissue <- dat %>% 
  group_by(Source, Year = factor(Year), 
           .drop = FALSE, .preserve = TRUE) %>% 
  summarise(n = length(Source))

```

```{r fig5-source-year-blues}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge()) +
  scale_fill_manual(values = blues[2:7], 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_blues.tif", 
       plot = source_year, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_blues.tif"))
```

```{r fig5-source-year-excel}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge()) +
  scale_fill_manual(values = excel_pal, 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_excel.tif", 
       plot = source_year, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_excel.tif"))
```

```{r fig5-source-year-greys}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black", 
           position = position_dodge()) +
  scale_fill_manual(values = greys, 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_greys.tif", 
       plot = source_year, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_greys.tif"))
```

### stacked
```{r fig5-source-year-stack-blues}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = blues[2:7], 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_stack_blues.tif", 
       plot = source_year, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_stack_blues.tif"))
```

```{r fig5- source-year-stack-excel}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = excel_pal, 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_stack_excel.tif", 
       plot = source_year, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_stack_excel.tif"))
```

```{r fig5-source-year-stack-greys}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = greys, 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_stack_greys.tif", 
       plot = source_year, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
grid.raster(readTIFF("figs/fig_5_Article_source_year_stack_greys.tif"))
```

## Figure 6 Articles by Test quality

```{r test-quality-prep}
summary_test <- dat %>% 
  group_by(test_results) %>% 
  summarise(n = length(test_results))

summary_test$x <- 1
tot <- sum(summary_test$n)
n <- summary_test$n
summary_test$lab_y <- c(n[1]/2,
                        n[1] + n[2]/2,
                        n[1] + n[2] + n[3]/2,
                        n[1] + n[2] + n[3] + n[4]/2,
                        n[1] + n[2] + n[3] + n[4] + n[5]/2)
```

```{r fig6-test-quality}
test_quality <- summary_test %>% 
  ggplot(aes(x = x, y = n, fill = rev(test_results)) ) +
  geom_bar(stat = "identity", 
           colour = "black", 
           width = 2) +
  geom_text(aes(x = x, y = lab_y, label = n),
            size = 6) +
  geom_text(aes(x = 2.2, y = lab_y, label = test_results),
            hjust = 0, size = 6 ) +
  scale_fill_manual(values = c(greys[3], greys[5], greys[6], greens[2], greens[4]),
                    name = "Test results") +
  xlim(0, 12)  +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme(panel.background = element_blank(),
        legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_blank(), 
        axis.ticks = element_blank(),
        panel.grid.minor.y = element_line(colour = "white", size = 0.3),
        panel.grid.major.x = element_blank()) 
ggsave("figs/fig_6_Article_test_quality.tif", 
       plot = test_quality, 
       device = device,
       width = fig_w_1.5, 
       height = fig_h,
       units = units,
       dpi = dpi)

```

## Figure 6 Articles by Phase and Test quality reported

### Stacked by number of articles
```{r}

summary_phase_test <- dat %>%
  group_by(Phase_condensed, test_results) %>% 
  summarise(n = length(Phase))
```

```{r fig7-phase-test-n}
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c(greens[4], greens[2], greys[6], greys[5],greys[3]),
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.title = element_text(size = 8, colour = "black"),
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"),
        legend.position = c(0.7, 0.8))
ggsave("figs/fig_7_Article_phase_test_quality_by_N.tif", 
       plot = phase_test, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### Stacked by percent of article

```{r fig7-phase-test-pc}
phase_test2 <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n)) +
  geom_bar(aes(fill = test_results), 
           stat = "identity", 
           colour = "black", 
           position = "fill") +
  scale_fill_manual(values = c(greens[4], greens[2]
                               , greys[6], greys[5],greys[3]),
                    name = "Test results", 
                    guide = guide_legend(nrow = 3, title = NULL )) +
  scale_y_continuous(name = "Proportion of Articles by Phase",
                     breaks = seq(0, 1.2, 0.2),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
  geom_text(data = summary_phase_condensed,
            aes(x = Phase_condensed, y = 1, vjust = -0.4,
                label = paste("n = ",n))) +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"),
        legend.position = "top") +
  coord_cartesian(clip = 'off')
ggsave("figs/fig_7_Article_phase_test_quality_by_PC.tif", 
       plot = phase_test2, 
       device = device,
       width = fig_w, 
       height = fig_h,
       units = units,
       dpi = dpi)
```

## Figure 9

There are some inconsistencies in the data file columns for markers (most have three associated columns (value, status and an unnamed one which appears to be a qualifier for the value and which I have named qualifier) but some have one a value but not status. It's not obv what the status should be in some cases.

The markers in this figure thus differ because I'm missed out the unknown status ones.

There's also a single "not stated" value remianing

```{r}
dat2 <- dat %>% 
  select(contains("_status")) %>% 
  rename_all(funs(stringr::str_replace(., fixed("_status"),"") )) %>% 
  gather(key = "marker", value = "status") %>%
  mutate(ISCT_pheno = recode_factor(marker,
                                CD73 = TRUE,
                                CD90 = TRUE,
                                CD105 = TRUE,
                                CD34 = TRUE,
                                CD45 = TRUE,
                                CD11b = TRUE,
                                CD14 = TRUE,
                                CD79a = TRUE,
                                CD19 = TRUE,
                                `HLA-DR` = TRUE,
                                .default = FALSE))  
# relevel the factor
dat2$marker <- fct_relevel(dat2$marker,
                           "viability", 
                           "CD73", 
                           "CD90", 
                           "CD105",
                           "CD34", 
                           "CD45", 
                           "CD11b",
                           "CD14", 
                           "CD79a",
                           "CD19",
                           "HLA-DR",
                           "CD133",
                           "CD166",
                           "CD29",
                           "CD44")
charc_marker <- dat2 %>%
  group_by(marker, status) %>% 
  summarise(n = length(marker))
charc_marker$marker <- fct_relevel(charc_marker$marker,
                           "viability", 
                           "CD73", 
                           "CD90", 
                           "CD105",
                           "CD34", 
                           "CD45", 
                           "CD11b",
                           "CD14", 
                           "CD79a",
                           "CD19",
                           "HLA-DR",
                           "CD133",
                           "CD166",
                           "CD29",
                           "CD44")
```

```{r}
charc_marker %>% 
  ggplot(aes(x = marker, y = n)) +
  geom_bar(aes(fill = status), 
           stat = "identity",
           position = "fill",
           colour = "white") +
  scale_fill_manual(values = blues[4:7], name = "Status") +
  scale_y_continuous(name = "Proportion of Articles") +
  scale_x_discrete(expand = c(0, 0), name = "Marker") +
  theme(panel.background = element_rect(fill = blues[2]),
        panel.grid = element_blank(),)

```

## Relationship between MOA and stem/stromal

```{r}
moa_isct_summary <- dat %>% 
  group_by(MOA, stem_stromal) %>% 
  summarise(n = length(MOA))

res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
                   res$method, ": p = ", round(res$p.value, 3))

```

```{r moa-isct-blues}
moa_isct <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = blues[2:5], 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x. TOP",
       caption = test_anno) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_x_moa_isct_blues.tif", 
       plot = moa_isct, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r moa-isct-excel}
moa_isct <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = excel_pal[1:4], 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x. TOP",
       caption = test_anno ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in")) 
 ggsave("figs/fig_x_moa_isct_excel.tif", 
       plot = moa_isct, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r moa-isct-greys}
moa_isct <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = greys[3:6], 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x. TOP",
       caption = test_anno ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_x_moa_isct_greys.tif", 
       plot = moa_isct, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

## Relationship between types of differentiation (OAC) and MOA

```{r}
table_info <- "There are five combinations for O, A and C potency. 'y' is demonstrated, 'm' is claimed but not demonstrated, 'n' is not mentioned. These were recoded into a single variable, 'potency'."

dat %>% 
  group_by(O, A, C, potency) %>% 
  summarise(n = length(O)) %>% 
  kable(caption = table_info) %>% 
  kable_styling() %>% 
  save_kable("figs/recode_differentiation_capacity.png")

```

```{r}
res <- table(dat$potency, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)

test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
                   res$method, ": p = ", round(res$p.value, 3))
```

```{r moa-potency-prep}
moa_potency_summary <- dat %>% 
  group_by(potency, MOA) %>% 
  summarise(n = length(MOA))
```

```{r moa_potency-blues}
moa_potency <- moa_potency_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = potency)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = blues[2:6], 
                    guide = guide_legend(nrow = 5, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x2. TOP",
       caption = test_anno) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_x2_moa_potency_blues.tif", 
       plot = moa_potency, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```

```{r moa_potency-excel}
moa_potency <- moa_potency_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = potency)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = excel_pal[2:6], 
                    guide = guide_legend(nrow = 5, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x2. TOP",
       caption = test_anno) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_x2_moa_potency_excel.tif", 
       plot = moa_potency, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```

```{r moa_potency-greys}
moa_potency <- moa_potency_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = potency)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = greys[2:6], 
                    guide = guide_legend(nrow = 5, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x2. TOP",
       caption = test_anno) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_x2_moa_potency_greys.tif", 
       plot = moa_potency, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```

## Claimed compliance vs categ compliance

```{r}
vals <- unique(dat$`ISCT compliance`)
ref <- dat$`Ref #`[is.na(dat$`ISCT compliance`)]
```

The values in `ISCT compliance` are: `r vals`
Probably the empty cell (formal NA in r) should be  "n/a" (a string). It's reference
`r ref`

```{r}

dat %>% 
  group_by(`ISCT compliance`,`ISCT claimed`) %>%
  summarise(n = length(`ISCT claimed`)) %>% 
  kable() %>% 
  kable_styling()

```
These results are so clear (all 14 of the papers that claim compliance do not demonstrate it; no other papers demonstrate it) that no further analysis is necessary.

## Relevance for indication, stem vs stromal
There are 50 different indications mostly with a single ref. This makes it difficult to deterimine if there is any relationalship between the nature of the indication and whether treatment was with stem of stromal cells.

```{r}
dat %>% 
  group_by(Indication, `Stem/Stromal`) %>% 
  summarise(n = length(`Stem/Stromal`)) %>% 
  ggplot(aes(x = reorder(Indication, n), y = n, fill = `Stem/Stromal`)) +
  geom_col() +
  coord_flip()
```

```{r}
ind <- dat %>% 
  group_by(Indication) %>% 
  summarise(n = length(potency)) %>% 
  filter(n > 1)

dat %>% 
  group_by(Indication,potency) %>% 
  summarise(n = length(Indication)) %>% 
  filter(n > 1)
```

### 2020-04-06 paper2_figures_viridis.Rmd
prep for final figures

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

# Figures specification
* titled
* cited in numerical order in the text using Arabic numbers. 
* no additional charges for color. 
* submitted as individual files
* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
* Figures may be submitted as multipart panels.
*  *.tif* or .eps 
* final publication size; 1-column width or, if necessary, 1½ column width. The * 2-column width should not be used unless necessary.
* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
* Calibri font sub sans serif Arial
* Multipanel labeled using uppercase 12-point Calibri Bold. 
* minimum text size of 6 points
* bold enough to be easily read after reduction, as should all symbols used in the * figure. Line or bar graphs or flow charts with text should be created in black and * white, not shades of gray, which are difficult to reproduce in even tones. If more * than two sets of data are represented, use of fill patterns or colors (not gray) is * suggested to present the data clearly.
* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for * combination halftones, and 1000 dpi for line art.

```{r pkg}
library(tidyverse)
library(RColorBrewer)
library(readxl)
library(kableExtra)
library(tiff)
library(grid)
library(patchwork)

```

```{r}

# palette
pal <- viridisLite::viridis(6)

# figure saving settings
units = "in"
fig_w <- 3.2
fig_w_1.5 <- 4.5
fig_h <- 4.5
fig_h_1.5 <- 4.5 * 1.5
dpi <- 300
device <- "tiff"

```

```{r import}
file <- here::here("data", "Meta-Analysis Data Collection.xlsx")

# added a row for column names more useful
# # skipped first two rows of of old col names

dat <- read_excel(file, sheet = "Data")

```

```{r tidy-data}
# recode country so those with one paper are
# "Other"
dat <- dat %>%
  mutate(Country2 = recode_factor(Country,
                                Brazil = "Brazil",
                                China = "China",
                                Denmark = "Denmark",
                                Egypt = "Egypt",
                                India = "India",
                                Japan = "Japan",
                                Korea = "Korea",
                                Netherlands = "Netherlands",
                                Poland = "Poland",
                                `Rep Korea` = "Rep Korea",
                                Russia = "Russia",
                                Spain = "Spain",
                                Taiwan = "Taiwan",
                                USA = "USA",
                                .default = "Other"))

dat <- dat %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

# test results - there is no "t" in the data file and there are more
# blanks values than t's in draft paper fig 6
dat <- dat %>%
  mutate(test_results = recode_factor(`Test Results?`,
                                       n = "Average value (n)",
                                       s = "Stated as 'standard phenotype' (s)",
                                       o = "Not discussed (o)",
                                       y = "Phenotypic markers reported (y)",
                                       t = "Tests done but not reported (t)"))
dat$test_results <- fct_relevel(dat$test_results,
                              "Phenotypic markers reported (y)", 
                              "Average value (n)",
                              "Tests done but not reported (t)",
                              "Stated as 'standard phenotype' (s)",
                              "Not discussed (o)")

# MOA - recode NS to Not stated
dat <- dat %>%
  mutate(MOA = recode_factor(MOA,
                             NS = "Not stated",
                             paracrine = "Paracrine",
                             immune = "Immune",
                             differentiation = "Differentiation",
                             multi = "Multiple"))

dat$MOA <- fct_relevel(dat$MOA,
                       "Paracrine",
                       "Immune",
                       "Differentiation",
                       "Multiple",
                       "Not stated")

# recode stem/stromal
dat <- dat %>%
  mutate(stem_stromal = recode_factor(`Stem/Stromal`,
                             `multipotent stromal` = "Multipotent Stromal",
                             other = "Other",
                             stem = "Stem",
                             stromal = "Stromal"))

dat$stem_stromal <- fct_relevel(dat$stem_stromal,
                                "Stromal",
                                "Stem",
                                "Multipotent Stromal",
                                "Other")

# Recode O, A and C into the 5 categories that appar 
dat <- dat %>%
  mutate(potency = ifelse(O == "y" &
                            A == "y" &
                            C == "y",
                          "Demonstrated tripotency",
                          ifelse(O == "n" &
                                   A == "n" &
                                   C == "n",
                                 "Not Stated",
                                 ifelse(O == "y" &
                                          A == "y" &
                                          C == "n",
                                        "Demonstrated bipotency (OA)",
                                        ifelse(O == "m"
                                               & A == "m" &
                                                 C == "n",
                                               "Claimed bipotency (OA)",
                                               ifelse(O == "m" &
                                                  A == "m" &
                                                  C == "m",
                                                  "Claimed tripotency", NA))))))

dat$potency <- fct_relevel(dat$potency,
                                "Demonstrated tripotency",
                                "Demonstrated bipotency (OA)",
                                "Claimed tripotency",
                                "Claimed bipotency (OA)",
                                "Not Stated")

######### code for "Data Tab copy v1.csv"
# # column indices for markers
# firstmarker <- which(colnames(dat) == "CD73")
# lastmarker <- which(colnames(dat) == "SSEA.4")
# # vector of marker names
# markers <- names(dat[firstmarker:lastmarker])
# 
# datnum <- dat %>% 
#   select(markers) %>% 
#   mutate_all(as.numeric) 
# 
# # add the non marker columns
# notmarkers <- which(!(colnames(dat) %in% markers))
# datnum <- cbind(dat[notmarkers], datnum)
# 
# 
# dat$Stem.Stromal <- factor(dat$Stem.Stromal)
# dat$Year <- factor(dat$Year)
# datnum$Stem.Stromal <- factor(datnum$Stem.Stromal)
# datnum$Year <- factor(datnum$Year)

```

```{r}
# cd values for

# note: file had missing value for Phas, this was looked up in "Meta-Analysis Data Collection.xlsx"
# as phase I/IIa
# note: ref 55, patient 6, marker CD45+/CD105+ contained value ND - I assumed this was no data.
# note - I have assumed range  is mean +/- se (not sd)
file <- here::here("data", "Paper 2 - Charts for Emma.xlsx")
cd_dat <- read_excel(file, sheet = "cd_values_single")
cd_dat2 <- read_excel(file, sheet = "cd_values_range")
```

```{r tidy-cd-data}
cd_dat <- cd_dat %>% 
  gather(key = marker, value = value, -Ref, -Phase, -patient, -notes)
cd_dat$value <- as.numeric(cd_dat$value)

cd_dat2 <- cd_dat2 %>% 
  gather(key = marker, value = value, -Ref, -Phase, -n)

for (i in 1:length(cd_dat2$value)) {
  temp <- strsplit(cd_dat2$value[i], split = "\\s.\\s") %>% unlist()
  cd_dat2$mean_value[i] <- as.numeric(temp[1])
  cd_dat2$se_value[i] <- as.numeric(temp[2])
}
cd_dat2 <- cd_dat2 %>% 
  filter(!is.na(value)) %>% 
  select(Ref, marker, mean_value, n, se_value, -Phase, -value)

```

# Figures

## Fig 1 - Article search funnel

```{r data-prep-fig1}
# create data
# short names for proof of method
orig <- data.frame(step_names = c("1.mesenchymal",
                                  "2.article",
                                  "3.cell tissue etc",
                                  "4.clinical etc",
                                  "5.not biotech etc",
                                  "6.exc conf etc"),
                   n = c(65706,
                         47031,
                         7814,
                         5502,
                         2055,
                         1986))

orig$step_names <- fct_relevel(orig$step_names,
                               "mesenchymal",
                               "article",
                               "cell tissue etc",
                               "clinical etc",
                               "not biotech etc",
                               "exc conf etc")

# prep polygons that connect
to_poly_orig <- orig %>%
  arrange(n) %>%
  mutate(
    group = row_number(),
    x1 = 0 + ((1 - n)/2),
    x4 = n + ((1 - n)/2),
    x2 = lag(x1), 
    x3 = lag(x4)) %>%
  mutate(
    x2 = ifelse(is.na(x2), x1, x2),
    x3 = ifelse(is.na(x3), x4, x3)
  ) %>%
  gather(xpoint, x, -step_names,-group, -n) %>%
  arrange(group, xpoint) %>%
  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))

# EXAMPLE
# Create the placement of the stages in the plot,
#  by just adding a 0.5 to each row number

labels <- orig %>%
  arrange(n) %>%
  mutate(y = row_number() + 0.5)

# modify the labels
labels$step_names2 <- c( "EXCLUDE conference proceedings,\nretracted papers",
                         "EXCLUDE CATEGORIES (NOT\nbiotechnology applied microbiology oncology\nhaematology, engineering biomedical)",
                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative medicine)",
                         "REFINE BY CATEGORY\ncell tissue engineering\nand transplantation",
                         "REFINE BY DOCUMENT TYPE\narticle",
                         "mesenchymal stem cells OR\nmesenchymal stromal cells OR\nMSC AND characterisation AND clinical")
```

```{r fig1}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = rev(pal))

ggsave("figs/fig_1_Article_search_funnel.tif", 
       plot = article_funnel, 
       device = device,
       width = fig_w, 
       height = 3.0,
       units = units,
       dpi = dpi)
```

## Figure 3 Articles by country

```{r country-prep}
summary_country <- dat %>%
  group_by(Country) %>% 
  summarise(n = length(Country))

```

```{r fig3-country-bar}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3],
           size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```
## Figure 4 Articles by Phase

### Six phase version

```{r phase-prep}
summary_phase <- dat %>%
  group_by(Phase) %>% 
  summarise(n = length(Phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))
summary_phase <- summary_phase %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

summary_phase_condensed <- dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

```

```{r fig4-phase}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3], size = 0) +
  xlab("") +
  geom_text(aes(y = n + 3, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 35, 5),
                     minor_breaks = seq(0, 35, 1),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase.tif", 
       plot = phase_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### Three phase

```{r fig4-phase-3}
phase_3_bar <- summary_phase_condensed %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3],size = 0) +
  xlab("") +
  geom_text(aes(y = n + 6, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 65, 5),
                     minor_breaks = seq(0, 65, 1),
                     limits = c(0, 65),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase_3.tif", 
       plot = phase_3_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

## Figure 5 Articles by Source-Year

Done with bars side-by-side or stacked.

### besides

```{r source_year_prep}
summary_tissue <- dat %>% 
  group_by(Source, Year = factor(Year), 
           .drop = FALSE) %>% 
  summarise(n = length(Source))

```

```{r fig5-source-year}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", size = 0, 
           position = position_dodge()) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 12, 1),
                    minor_breaks = seq(0, 12, 1),
                    limits = c(0, 12),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year.tif", 
       plot = source_year, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### stacked
```{r fig5-source-year-stack}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal,
                    guide = guide_legend(nrow = 2, title = NULL )) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 18, 1),
                    minor_breaks = seq(0, 18, 1),
                    limits = c(0, 18),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.title = element_text(size = 6, colour = "black"),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.1, "in"))
ggsave("figs/fig_5_Article_source_year_stack.tif", 
       plot = source_year, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

## Figure 6 Articles by Test quality

```{r test-quality-prep}
summary_test <- dat %>% 
  group_by(test_results) %>% 
  summarise(n = length(test_results))

summary_test$x <- 1
tot <- sum(summary_test$n)
n <- summary_test$n
summary_test$lab_y <- c(n[1]/2,
                        n[1] + n[2]/2,
                        n[1] + n[2] + n[3]/2,
                        n[1] + n[2] + n[3] + n[4]/2,
                        n[1] + n[2] + n[3] + n[4] + n[5]/2)
```

## Figure 7 Articles by Phase and Test quality reported

### Stacked by number of articles
```{r}

summary_phase_test <- dat %>%
  group_by(Phase_condensed, test_results) %>% 
  summarise(n = length(Phase))
```

```{r fig7-phase-test-n}
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
#  labs(subtitle = "A") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 8),
        legend.position = "none")
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"))

```

### Stacked by percent of article

```{r fig7-phase-test-pc}
phase_test2 <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n)) +
  geom_bar(aes(fill = test_results), 
           stat = "identity", 
           size = 0, 
           position = "fill") +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Proportion of Articles",
                     breaks = seq(0, 1, 0.2),
                #     limits = c(0, 1.2),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
  geom_text(data = summary_phase_condensed,
            aes(x = Phase_condensed, y = 1.05, vjust = 1,
                label = paste("n = ",n))) +
#  labs(subtitle = "B") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
      #  plot.title = element_text(hjust = 0, size = 8),
       legend.position = "none")

phase_test_both <- phase_test + phase_test2 + guide_area() +
  plot_annotation(title = "Wilson, Alison, Figure 7. TOP",
                  tag_levels = "A") +
  theme(legend.position = "top") +
  guides(fill = guide_legend(nrow = 2, title.position = "top"))

ggsave("figs/fig_7_characterisation_by_phase.tif", 
       plot = phase_test_both, 
       device = device,
       width = fig_w_1.5, 
       height = fig_h,
       units = units,
       dpi = dpi)
```

## Figure 9

```{r}
# data incoming
```

```{r}
# charc_marker %>% 
#   ggplot(aes(x = marker, y = n)) +
#   geom_bar(aes(fill = status), 
#            stat = "identity",
#            position = "fill",
#            colour = "white") +
#   scale_fill_manual(values = blues[4:7], name = "Status") +
#   scale_y_continuous(name = "Proportion of Articles") +
#   scale_x_discrete(expand = c(0, 0), name = "Marker") +
#   theme(panel.background = element_rect(fill = blues[2]),
#         panel.grid = element_blank(),)

```

## Relationship between MOA and stem/stromal

```{r}
moa_isct_summary <- dat %>% 
  group_by(MOA, stem_stromal) %>% 
  summarise(n = length(MOA))

res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
                   res$method, ": p = ", round(res$p.value, 3))

```

```{r moa-isct}
moa_isct <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x. TOP") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))
ggsave("figs/fig_x_moa_isct.tif", 
       plot = moa_isct, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```
## Relationship between types of differentiation (OAC) and MOA

```{r}
table_info <- "There are five combinations for O, A and C potency. 'y' is demonstrated, 'm' is claimed but not demonstrated, 'n' is not mentioned. These were recoded into a single variable, 'potency'."

dat %>% 
  group_by(O, A, C, potency) %>% 
  summarise(n = length(O)) %>% 
  kable(caption = table_info) %>% 
  kable_styling() %>% 
  save_kable("figs/recode_differentiation_capacity.png")

```

```{r}
res <- table(dat$potency, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)

test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
                   res$method, ": p = ", round(res$p.value, 3))
```

```{r moa-potency-prep}
moa_potency_summary <- dat %>% 
  group_by(potency, MOA) %>% 
  summarise(n = length(MOA))
```

```{r moa_potency}
moa_potency <- moa_potency_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = potency)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 5, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x2. TOP") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))
ggsave("figs/fig_x2_moa_potency.tif", 
       plot = moa_potency, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```

```{r}
cd_dat_summary <- cd_dat %>% 
  group_by(Ref, marker) %>% 
  summarise(mean_value = mean(value),
            n = length(value),
            se_value = sd(value)/sqrt(n))
str(cd_dat_summary)
# length(unique(cd_dat$marker)) *length(unique(cd_dat$Ref))

# bind the range and the sinlge value dataframes
cd_dat_summary <- rbind(data.frame(cd_dat_summary), cd_dat2)

```

```{r}
# count the number of refs that have values
cd_refs_by_marker <- cd_dat_summary %>% 
  group_by(marker) %>%
  summarise(n_refs = length(mean_value[!is.na(mean_value)]))

cd_refs_by_marker$marker
isct <- c("Viability","CD73", "CD90", "CD105", "CD34", "CD45" , "CD11b", "CD14" , "CD79α", "CD19", "HLA-DR")
cd_refs_by_marker$ISCT <- "Other marker"
cd_refs_by_marker$ISCT[cd_refs_by_marker$marker %in% isct] <- "ISCT phenotype marker"

cd_refs_by_marker$ISCT <- fct_relevel(cd_refs_by_marker$ISCT,
                              "ISCT phenotype marker",
                              "Other marker")

```

```{r cd-refs-bar}
cd_refs_bar <- cd_refs_by_marker %>% 
  arrange(ISCT, n_refs) %>%
         mutate(marker = factor(marker, levels = marker) ) %>% 
  ggplot(aes(x = reorder(marker, ISCT), y = n_refs, fill = ISCT )) +
  geom_bar(stat = "identity",  size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 15, 1),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 15),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_manual(values = pal[c(5, 2)], 
                    name = NULL) +
  labs(title = "Wilson, Alison, Figure X3. TOP" ) +
  annotate("segment", x = 0.5, xend = 10.5, 
           y = 14, yend = 14,
           colour = "black", size = 1) +
  annotate("segment", x = 0.58, xend = 0.58, 
           y = 14, yend = 13.5,
           colour = "black", size = 1) +
  annotate("segment", x = 10.38, xend = 10.38, 
           y = 14, yend = 13.5,
           colour = "black", size = 1) +
  annotate("text", x = 3,  y = 10, 
           label = "ISCT phenotype\nmarker", size = 4) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_x3_cd_refs_bar.tif", 
       plot = cd_refs_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}

cd_dat_summary_values <- cd_dat_summary %>% 
  filter(!is.na(mean_value))

cd_dat_summary_values$ISCT <- "Other marker"
cd_dat_summary_values$ISCT[cd_dat_summary_values$marker %in% isct] <- "ISCT phenotype marker"

cd_dat_summary_values$ISCT <- fct_relevel(cd_dat_summary_values$ISCT,
                              "ISCT phenotype marker",
                              "Other marker")
```

```{r}
cd_values_point_isct <- cd_dat_summary_values %>% 
  filter(ISCT == "ISCT phenotype marker") %>% 
  ggplot(aes(x = marker, y = mean_value)) +
  geom_pointrange(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                  position = position_jitter(width = 0.5), shape = 20) +
  xlab("") +
  scale_y_continuous(name = "Value reported", 
                     breaks = seq(0, 110, 10),
                     minor_breaks = seq(0, 110, 10),
                     limits = c(0, 110),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure X4. TOP" ) +
  geom_vline(xintercept = seq(1.5, 10.5, 1), linetype = "longdash") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4))
ggsave("figs/fig_x4_cd_values_isct.tif", 
       plot = cd_values_point_isct, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
cd_values_point_other <- cd_dat_summary_values %>% 
  filter(ISCT == "Other marker") %>% 
  ggplot(aes(x = marker, y = mean_value)) +
  geom_pointrange(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                  position = position_jitter(width = 0.5), shape = 20) +
  xlab("") +
  scale_y_continuous(name = "Value reported", 
                     breaks = seq(0, 110, 10),
                     minor_breaks = seq(0, 110, 10),
                     limits = c(0, 110),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure X4. TOP" ) +
  geom_vline(xintercept = seq(1.5, 10.5, 1), linetype = "longdash") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4))
ggsave("figs/fig_x5_cd_values_isct.tif", 
       plot = cd_values_point_other, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### 2020-04-06 scripts/emma.R

@@ -1,0 +1,135 @@
+# Emma - analysis
+# packaes needed
+library(tidyverse)
+
+# this sets your working directory to the location of emma.R
+# all the other file paths are given relative to this script
+here::here()
+
+
+# import
+# character values will be read as character datatypes rather than factors
+# which makes processing easier in the first instance
+# note: last record contained no info except: 
+#     "compares different papers on bone marrow MSCs, 
+#     doesn't say anything about prep of cells"
+#   This was deleted (perhaps it belongs on another line?)
+
+dat <- read.csv("../data/Data Tab copy v1.csv", stringsAsFactors = FALSE)
+
+# column indices for markers
+firstmarker <- which(colnames(dat) == "CD73")
+lastmarker <- which(colnames(dat) == "SSEA.4")
+# vector of marker names
+markers <- names(dat[firstmarker:lastmarker])
+
+datnum <- dat %>% 
+  select(markers) %>% 
+  mutate_all(list(num = ~ as.numeric(.))) 
+
+# do the same for binary coding: 0 or 1
+
+dat <- cbind(dat, datnum[,24:46])
+dat$Stem.Stromal <- factor(dat$Stem.Stromal)
+dat$Year <- factor(dat$Year)
+
+# stacked - my preference
+ggplot(data = dat, aes(x = Year, fill = Stem.Stromal)) +
+  geom_bar(colour = "black") +
+  theme_classic() +
+  ylab("Frequency") +
+  xlab("Year")
+
+              
+# besides data summary
+datsum <- dat %>% 
+  group_by(Stem.Stromal, Year, .drop = FALSE) %>% 
+  summarise(n = length(Ref..))
+  
+# besides
+ggplot(data = datsum, aes(x = Year, y = n, fill = Stem.Stromal)) +
+  geom_bar(stat = "identity", position = position_dodge()) +
+  theme_classic() +
+  ylab("Frequency") +
+  xlab("Year")
+
+table(dat$Phase)
+ggplot(data = dat, aes(x = Phase, fill = Stem.Stromal)) +
+  geom_bar(colour = "black") +
+  theme_classic() +
+  ylab("Frequency") +
+  xlab("Phase")
+
+datnum2 <- datnum %>% 
+  select(ends_with("_num")) %>% 
+  gather(key = marker, value = value)
[…]

### 2020-04-06 scripts/working.R

@@ -1,0 +1,96 @@
+stages <- tibble(
+  clicks = 1,
+  signups = .47,
+  cart = .09,
+  buys = .05
+) %>%
+  gather(stage, percent)
+
+stages
+to_poly <- stages %>%
+  arrange(percent) %>%
+  mutate(
+    group = row_number(),
+    x1 = 0 + ((1 - percent)/2),
+    x4 = percent + ((1 - percent)/2),
+    x2 = lag(x1), 
+    x3 = lag(x4)
+  ) %>%
+  mutate(
+    x2 = ifelse(is.na(x2), x1, x2),
+    x3 = ifelse(is.na(x3), x4, x3)
+  ) %>%
+  gather(key = xpoint, value = x, -stage,-group, -percent) %>%
+  arrange(group, xpoint) %>%
+  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))
+
+to_poly
+
+#########################
+orig <- data.frame(step_names = c("mesenchymal",
+                                  "article",
+                                  "cell tissue etc",
+                                  "clinical etc",
+                                  "not biotech etc"),
+                   n = c(65706,
+                         47031,
+                         7814,
+                         5502,
+                         2055))
+
+orig$step_names <- fct_relevel(orig$step_names,
+                               "mesenchymal",
+                               "article",
+                               "cell tissue etc",
+                               "clinical etc",
+                               "not biotech etc")
+# prep polygons that connect
+to_poly_orig <- orig %>%
+  arrange(n) %>%
+  mutate(
+    group = row_number(),
+    x1 = 0 + ((1 - n)/2),
+    x4 = n + ((1 - n)/2),
+    x2 = lag(x1), 
+    x3 = lag(x4)) %>%
+  mutate(
+    x2 = ifelse(is.na(x2), x1, x2),
+    x3 = ifelse(is.na(x3), x4, x3)
+  ) %>%
+  gather(xpoint, x, -step_names,-group, -n) %>%
+  arrange(group, xpoint) %>%
+  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))
+
+
+# EXAMPLE
+# Create the placement of the stages in the plot,
+#  by just adding a 0.5 to each row number
+
+labels <- orig %>%
+  arrange(n) %>%
+  mutate(y = row_number() + 0.5)
+
+cbPalette <- brewer.pal(6,"Blues")
+
+to_poly_orig %>%
+  ggplot() +
+  geom_polygon(aes(x,
[…]

### 2020-04-17 paper2_figures_viridis_checked.Rmd
all updated with check data; figs 1, 3, 4, 5,6,7 7alt,8,9,10 are done

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

# Figures specification
* titled
* cited in numerical order in the text using Arabic numbers. 
* no additional charges for color. 
* submitted as individual files
* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
* Figures may be submitted as multipart panels.
*  *.tif* or .eps 
* final publication size; 1-column width or, if necessary, 1½ column width. The * 2-column width should not be used unless necessary.
* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
* Calibri font sub sans serif Arial
* Multipanel labeled using uppercase 12-point Calibri Bold. 
* minimum text size of 6 points
* bold enough to be easily read after reduction, as should all symbols used in the * figure. Line or bar graphs or flow charts with text should be created in black and * white, not shades of gray, which are difficult to reproduce in even tones. If more * than two sets of data are represented, use of fill patterns or colors (not gray) is * suggested to present the data clearly.
* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for * combination halftones, and 1000 dpi for line art.

```{r pkg}
library(tidyverse)
library(RColorBrewer)
library(readxl)
library(kableExtra)
library(tiff)
library(grid)
library(patchwork)

```

```{r}

# palette
pal <- viridisLite::viridis(6)

# figure saving settings
units = "in"
fig_w <- 3.2
fig_w_1.5 <- 4.5
fig_w_2 <- 5.8
fig_h <- 4.5
fig_h_1.5 <- 4.5 * 1.5
dpi <- 300
device <- "tiff"

```

```{r import}
# file <- here::here("data", "Checked Data.xlsx")
# 
# # added a row for column names more useful
# # # skipped first two rows of of old col names
# 
# dat <- read_excel(file, sheet = "Checked Data")

```

```{r tidy-data}
# recode country so those with one paper are
# "Other"
# dat <- dat %>%
#   mutate(Country2 = recode_factor(Country,
#                                 Brazil = "Brazil",
#                                 China = "China",
#                                 Denmark = "Denmark",
#                                 Egypt = "Egypt",
#                                 India = "India",
#                                 Japan = "Japan",
#                                 Korea = "Korea",
#                                 Netherlands = "Netherlands",
#                                 Poland = "Poland",
#                                 `Rep Korea` = "Rep Korea",
#                                 Russia = "Russia",
#                                 Spain = "Spain",
#                                 Taiwan = "Taiwan",
#                                 USA = "USA",
#                                 .default = "Other"))
```

```{r}
# dat <- dat %>%
#   mutate(Phase_condensed = recode_factor(Phase,
#                                I = "I",
#                                `I/IIa` = "I",
#                                `I/II` = "I",
#                                 II = "II",
#                                 IIa = "II",
#                                IIb = "II",
#                                III = "III"))
```

```{r}
# dat <- dat %>%
#   mutate(test_results = recode_factor(`Test Results?`,
#                                        n = "Average value (n)",
#                                        s = "Stated as 'standard phenotype' (s)",
#                                        o = "Not discussed (o)",
#                                        y = "Phenotypic markers reported (y)",
#                                        t = "Tests done but not reported (t)"))
# dat$test_results <- fct_relevel(dat$test_results,
#                               "Phenotypic markers reported (y)", 
#                               "Average value (n)",
#                               "Tests done but not reported (t)",
#                               "Stated as 'standard phenotype' (s)",
#                               "Not discussed (o)")
```

```{r}
# MOA - recode NS to Not stated
# dat <- dat %>%
#   mutate(MOA = recode_factor(MOA,
#                              NS = "Not stated",
#                              paracrine = "Paracrine",
#                              immune = "Immune",
#                              differentiation = "Differentiation",
#                              multi = "Multiple"))
# 
# dat$MOA <- fct_relevel(dat$MOA,
#                        "Paracrine",
#                        "Immune",
#                        "Differentiation",
#                        "Multiple",
#                        "Not stated")
```

```{r}
# recode stem/stromal
# dat <- dat %>%
#   mutate(stem_stromal = recode_factor(`Stem/Stromal`,
#                              `multipotent stromal` = "Multipotent Stromal",
#                              regenerative = "Regenerative",
#                              stem = "Stem",
#                              stromal = "Stromal"))
# 
# dat$stem_stromal <- fct_relevel(dat$stem_stromal,
#                                 "Stromal",
#                                 "Stem",
#                                 "Multipotent Stromal",
#                                 "Regenerative")
# note: no longer an 'other' category, new regerative category
```

```{r}

# # Recode O, A and C into the 5 categories that appar 
# dat <- dat %>%
#   mutate(differentiation = ifelse(O == "y" &
#                             A == "y" &
#                             C == "y",
#                           "Demonstrated tripotency",
#                           ifelse(O == "n" &
#                                    A == "n" &
#                                    C == "n",
#                                  "Not Stated",
#                                  ifelse(O == "y" &
#                                           A == "y" &
#                                           C == "n",
#                                         "Demonstrated bipotency (OA)",
#                                         ifelse(O == "y" &
#                                                  A == "n" &
#                                                  C == "n",
#                                                "Demonstrated potency (O)",
#                                                ifelse(O == "m"
#                                                       & A == "m" &
#                                                         C == "n",
#                                                       "Claimed bipotency (OA)",
#                                                       ifelse(O == "m" &
#                                                                A == "m" &
#                                                                C == "m",
#                                                              "Claimed tripotency", NA)))))))        
# 
# dat$differentiation <- fct_relevel(dat$differentiation,
#                                 "Demonstrated tripotency",
#                                 "Demonstrated bipotency (OA)",
#                                 "Demonstrated potency (O)",
#                                 "Claimed tripotency",
#                                 "Claimed bipotency (OA)",
#                                 "Not Stated")                        
```

```{r}
# Recode O, A and C into 2 categories, all n = No, anything else = Yes 
# dat <- dat %>%
#   mutate(differentiation2 = ifelse(O == "n" &
#                                    A == "n" &
#                                    C == "n",
#                                  "No", "Yes"))      
# 
# dat$differentiation2<- fct_relevel(dat$differentiation2,
#                                 "No","Yes")                        
```
## write to file
```{r}
# file <- "data/checked_processed.csv"
# write_csv(dat, file)
```

# Read in the processed and corrected data

```{r}
file <- "data/checked_processed_aw_corrections.csv"
dat <- read_csv(file)
```

```{r}
dat <- dat %>%
  mutate(test_results = recode_factor(`Test Results?`,
                                       n = "Average value (n)",
                                       s = "Stated as 'standard phenotype' (s)",
                                       o = "Not discussed (o)",
                                       y = "Phenotypic markers reported (y)",
                                       t = "Tests done but not reported (t)"))
dat$test_results <- fct_relevel(dat$test_results,
                              "Phenotypic markers reported (y)",
                              "Average value (n)",
                              "Tests done but not reported (t)",
                              "Stated as 'standard phenotype' (s)",
                              "Not discussed (o)")
```

```{r}
# add a count of the number of markers tested for "Average value (n)". select columns like _test
test_cols <- names(select(dat, ends_with("_test")) )
dat <- dat %>%
  mutate(marker_count = rowSums(.[test_cols] == "p"))

```

```{r}

dat %>% group_by(MOA) %>% summarise(n = length(MOA))

dat$MOA <- fct_relevel(dat$MOA,
                       "Paracrine",
                       "Immune",
                       "Differentiation",
                       "Multiple",
                       "Not stated")
```

```{r}
dat %>% group_by(stem_stromal) %>% summarise(n = length(stem_stromal))

dat$stem_stromal <- fct_relevel(dat$stem_stromal,
                                "Stromal",
                                "Stem",
                                "Multipotent Stromal",
                                "Regenerative")
```

```{r}
# cd values for

# note: file had missing value for Phas, this was looked up in "Meta-Analysis Data Collection.xlsx"
# as phase I/IIa
# note: ref 55, patient 6, marker CD45+/CD105+ contained value ND - I assumed this was no data.
# note - I have assumed range  is mean +/- se (not sd)
# file <- here::here("data", "Paper 2 - Charts for Emma.xlsx")
# cd_dat <- read_excel(file, sheet = "cd_values_single")
# cd_dat2 <- read_excel(file, sheet = "cd_values_range")
```

```{r tidy-cd-data}
# cd_dat <- cd_dat %>% 
#   gather(key = marker, value = value, -Ref, -Phase, -patient, -notes)
# cd_dat$value <- as.numeric(cd_dat$value)
# 
# cd_dat2 <- cd_dat2 %>% 
#   gather(key = marker, value = value, -Ref, -Phase, -n)
# 
# for (i in 1:length(cd_dat2$value)) {
#   temp <- strsplit(cd_dat2$value[i], split = "\\s.\\s") %>% unlist()
#   cd_dat2$mean_value[i] <- as.numeric(temp[1])
#   cd_dat2$se_value[i] <- as.numeric(temp[2])
# }
# cd_dat2 <- cd_dat2 %>% 
#   filter(!is.na(value)) %>% 
#   select(Ref, marker, mean_value, n, se_value, -Phase, -value)

```

```{r}
dat %>% group_by(O) %>% 
  summarise(n = length(O), pc = n/84)
```
```{r}
dat %>% group_by(A) %>% 
  summarise(n = length(A), pc = n/84)
```
```{r}
dat %>% group_by(C) %>% 
  summarise(n = length(C), pc = n/84)
```
```{r}
dat %>% group_by(differentiation) %>% 
  summarise(n = length(differentiation), pc = n/84)
```

# Figures

## Fig 1 - Article search funnel

```{r data-prep-fig1}
# create data
# short names for proof of method
orig <- data.frame(step_names = c("1.mesenchymal",
                                  "2.article",
                                  "3.cell tissue etc",
                                  "4.clinical etc",
                                  "5.not biotech etc",
                                  "6.exc conf etc"),
                   n = c(65706,
                         47031,
                         7814,
                         5502,
                         2055,
                         1986))

orig$step_names <- fct_relevel(orig$step_names,
                               "mesenchymal",
                               "article",
                               "cell tissue etc",
                               "clinical etc",
                               "not biotech etc",
                               "exc conf etc")

# prep polygons that connect
to_poly_orig <- orig %>%
  arrange(n) %>%
  mutate(
    group = row_number(),
    x1 = 0 + ((1 - n)/2),
    x4 = n + ((1 - n)/2),
    x2 = lag(x1), 
    x3 = lag(x4)) %>%
  mutate(
    x2 = ifelse(is.na(x2), x1, x2),
    x3 = ifelse(is.na(x3), x4, x3)
  ) %>%
  gather(xpoint, x, -step_names,-group, -n) %>%
  arrange(group, xpoint) %>%
  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))

# EXAMPLE
# Create the placement of the stages in the plot,
#  by just adding a 0.5 to each row number

labels <- orig %>%
  arrange(n) %>%
  mutate(y = row_number() + 0.5)

# modify the labels
labels$step_names2 <- c( "EXCLUDE conference proceedings,\nretracted papers",
                         "EXCLUDE CATEGORIES (NOT\nbiotechnology applied microbiology oncology\nhaematology, engineering biomedical)",
                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative medicine)",
                         "REFINE BY CATEGORY\ncell tissue engineering\nand transplantation",
                         "REFINE BY DOCUMENT TYPE\narticle",
                         "mesenchymal stem cells OR\nmesenchymal stromal cells OR\nMSC AND characterisation AND clinical")
```

```{r fig1}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = rev(pal))

ggsave("figs/fig_1_Article_search_funnel.tif", 
       plot = article_funnel, 
       device = device,
       width = fig_w, 
       height = 3.0,
       units = units,
       dpi = dpi)
```

## Figure 3 Articles by country

```{r country-prep}
summary_country <- dat %>%
  group_by(Country) %>% 
  summarise(n = length(Country))

```

```{r fig3-country-bar}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3],
           size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```
## Figure 4 Articles by Phase

### Eight phase version

```{r phase-prep}

summary_phase <- dat %>%
  group_by(Phase) %>% 
  summarise(n = length(Phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))
summary_phase <- summary_phase %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                               `I/II` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III",
                               NS = "NS"))

summary_phase_condensed <- dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

```

```{r fig4-phase}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3], size = 0) +
  xlab("") +
  geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 1),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_4_Article_phase.tif", 
       plot = phase_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### Three phase

```{r fig4-phase-3}
# phase_3_bar <- summary_phase_condensed %>% 
#   ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
#   geom_bar(stat = "identity", fill = pal[3],size = 0) +
#   xlab("") +
#   geom_text(aes(y = n + 6, label = pc) ) +
#   scale_y_continuous(name = "Number of Articles", 
#                      breaks = seq(0, 65, 5),
#                      minor_breaks = seq(0, 65, 1),
#                      limits = c(0, 65),
#                      expand = c(0, 0)) +
#   scale_x_discrete(expand = c(0, 0)) +
#   labs(title = "Wilson, Alison, Figure 4. TOP" ) +
#   theme_classic() +
#   theme(axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 8, colour = "black"),
#         axis.ticks.y = element_blank(),
#         axis.text.y  = element_text(size = 8, colour = "black"),
#         panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         plot.title = element_text(hjust = 0, size = 4)) +
#   coord_flip()
# 
# ggsave("figs/fig_4_Article_phase_3.tif", 
#        plot = phase_3_bar, 
#        device = device,
#        width = fig_w, 
#        height = fig_w,
#        units = units,
#        dpi = dpi)

```

## Figure 5 Articles by Source-Year

```{r source_year_prep}
summary_tissue <- dat %>% 
  group_by(Source, Year = factor(Year), 
           .drop = FALSE) %>% 
  summarise(n = length(Source))
dat %>% 
  group_by(Source, 
           .drop = FALSE) %>% 
  summarise(n =length(Source), pc = n/84)

```

### stacked
```{r fig5-source-year-stack}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal[c(1,3,5,6)],
                    guide = guide_legend(nrow = 3, title = NULL )) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 20, 2),
                    minor_breaks = seq(0, 20, 2),
                    limits = c(0, 20),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = c(0.2, 0.9),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))

ggsave("figs/fig_5_Article_source_year_stack.tif", 
       plot = source_year, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

## Figure 6 - three panels

### panel 1: Articles by Test quality

```{r test-quality-prep}
summary_test <- dat %>% 
  group_by(test_results) %>% 
  summarise(n = length(test_results),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

```

```{r testquality}
test_bar <- summary_test %>% 
  ggplot(aes(x = reorder(test_results, n), y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  xlab("") +
  geom_text(aes(y = n + 6, label = pc) ) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 50, 5),
                     minor_breaks = seq(0, 50, 1),
                     limits = c(0, 50),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0),
                   labels = c("Stated as 'standard\nphenotype' (s)",
                              "Phenotypic markers\nreported (y)",
                              "Tests done but\nnot reported (t)",
                              "Not discussed (o)",
                              "Average value (n)")) +
  labs(subtitle = "A") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4),
        plot.margin = margin(r = 0.1, b = 0.1, l = 0, unit="in")) +
  coord_flip()

# ggsave("figs/fig_6_Article_test_quality.tif", 
#        plot = test_bar, 
#        device = device,
#        width = fig_w, 
#        height = fig_w,
#        units = units,
#        dpi = dpi)

```

### panel 2 how many markers had average values  
```{r}
summary_marker_count <- dat %>% 
  filter(test_results == "Average value (n)") %>%
  group_by(marker_count) %>% 
  summarise(n = length(marker_count))

```

```{r markercount}
marker_bar <- summary_marker_count %>% 
  ggplot(aes(x = factor(marker_count), y = n)) +
  geom_bar(stat = "identity", fill = pal[2], size = 0) +
  scale_y_continuous(name = "Number of\n'Average value (n)' Articles ", 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 12),
                     expand = c(0, 0)) +
  scale_x_discrete(name = "Number of markers\nreported by an article",
                   expand = c(0, 0)) +
  labs(subtitle = "B") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.margin = margin(r = 0.2, t = 0,l = 0, unit="in")) 
```

### panel 3  Articles by Phase and Test quality reported (previously fig7 a)

### Stacked by number of articles
```{r}

dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = n/84)

summary_phase_test <- dat %>%
  group_by(Phase_condensed, test_results) %>% 
  summarise(n = length(Phase_condensed))
```

```{r phasetest}
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
 labs(subtitle = "C") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 8),
        legend.position = "none", 
        plot.margin = margin(r = 0.3, l = 0.1, t = 0, unit="in"))

```

### Stacked by percent of article

```{r fig7-phase-test-pc}
# phase_test2 <- summary_phase_test %>% 
#   ggplot(aes(x = Phase_condensed, y = n)) +
#   geom_bar(aes(fill = test_results), 
#            stat = "identity", 
#            size = 0, 
#            position = "fill") +
#   scale_fill_manual(values = pal,
#                     name = "Test results") +
#   scale_y_continuous(name = "Proportion of Articles",
#                      breaks = seq(0, 1, 0.2),
#                 #     limits = c(0, 1.2),
#                      expand = c(0, 0)) +
#   scale_x_discrete(expand = c(0, 0), name = "Phase") +
#   geom_text(data = summary_phase_condensed,
#             aes(x = Phase_condensed, y = 1.05, vjust = 1,
#                 label = paste("n = ",n)),size=3) +
#  labs(subtitle = "B") +
#   theme_classic() +
#   theme(axis.text.x = element_text(size = 8, colour = "black"),
#         axis.text.y  = element_text(size = 8, colour = "black"),
#         panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         #  plot.title = element_text(hjust = 0, size = 8),
#         legend.position = "none",
#         plot.margin = margin(r = 0, l = 0, unit="in"))

```

```{r fig6}

layout <- "
aaaaaaa#
aaaaaaa#
aaaaaaa#
#bbbbccc
#bbbbccc
#bbbbccc
#bbbbccc
#bbbbccc
"

fig6 <- test_bar + marker_bar + phase_test + 
  plot_layout(design = layout) +
  plot_annotation(title = "Wilson, Alison, Figure 6. TOP")&
    theme(text = element_text(size = 8, hjust = 0))

ggsave("figs/fig_6.tif", 
       plot = fig6, 
       device = device,
       width = fig_w_2, 
       height = fig_h,
       units = units,
       dpi = dpi)

```

```{r}
dat
```

## Figure 7 Characterisation by marker.
```{r}

# select the test columns and count the number of articles for each marker and category
test_cols

charact_by_marker_ref <- dat %>% 
  select(ends_with("_test"), `Ref #`) %>% 
  pivot_longer(cols = -`Ref #`, names_to = "marker", values_to = "status")

# process the names to remove _test

charact_by_marker_ref <- charact_by_marker_ref %>% 
  mutate(marker2 = str_replace(marker, "_test", ""))

# change levels of status and markers.
# markers
# process test_col names
test_cols <- str_replace(test_cols, "_test", "")
# set the levels in that order
charact_by_marker_ref$marker2 <- factor(charact_by_marker_ref$marker2, levels = test_cols)

# status
# recode status
charact_by_marker_ref <- charact_by_marker_ref %>%
  mutate(test_status = recode_factor(status,
                             p = "Performed, value reported",
                             m = "Performed, no value reported",
                             n = "Not mentioned"))

charact_by_marker_ref$test_status <- fct_relevel(charact_by_marker_ref$test_status,
                                                     "Not mentioned",
                                                     "Performed, no value reported",
                                                     "Performed, value reported")

charact_by_marker_summary <- charact_by_marker_ref %>% 
  group_by(marker2, test_status) %>% 
  summarise(n = length(marker2))

```

```{r}
fig7 <- charact_by_marker_summary %>% 
  ggplot() +
  geom_bar(aes(x = marker2, y = n, fill = test_status),
           stat = "identity", width = 0.6) +
  scale_fill_manual(values =  pal[c(1, 2, 5)],
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 90, 10),
                     minor_breaks = seq(0, 90, 10),
                     limits = c(0, 90),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = "Characterisation attribute") +
  geom_rect(xmin = 1.5, xmax = 11.5,
            ymin = -Inf, ymax = Inf,
            size = 1, linetype = 1, 
            colour = "black", alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 6, colour = "black",
                                   angle = -60, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

ggsave("figs/fig_7_charact_by_marker.tif", 
       plot = fig7, 
       device = device,
       width = fig_w_2, 
       height = fig_h,
       units = units,
       dpi = dpi)

```

```{r}
#alt fig
fig7alt <- charact_by_marker_ref %>% 
  ggplot() +
  geom_tile(aes(x = factor(`Ref #`), y = marker2 , fill = test_status),
            colour = "white")+
    scale_fill_manual(values =  pal[c(1, 2, 5)],
                    name = "Test results",
                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
  scale_x_discrete(name = "Reference",
                     expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute") +
  geom_rect(ymin = 1.5, ymax = 11.5,
            xmin = -Inf, xmax = Inf,
            size = 1, linetype = 1,
            colour = pal[6], alpha = 0) +
  labs(title = "Wilson, Alison, Figure 7ALT. TOP" ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 5, colour = "black", 
                                   angle = 90, hjust = 0, vjust = 0.3),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.2, "in"))

ggsave("figs/fig_7_alt.tif", 
       plot = fig7alt, 
       device = device,
       width = fig_w_2, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

# Figure 8

# Figure 9

## Relationship between MOA and stem/stromal

```{r}
moa_isct_summary <- dat %>% 
  group_by(MOA, stem_stromal) %>% 
  summarise(n = length(MOA))

dat %>% 
  group_by(stem_stromal) %>% 
  summarise(n = length(stem_stromal),
            pc = n/84)

res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
                   res$method, ": p = ", round(res$p.value, 3))

```

```{r moa-isct}
moa_isct <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure 9. TOP") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                   angle = -60, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))
ggsave("figs/fig_9_moa_isct.tif", 
       plot = moa_isct, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

## Figure 10 assocation between differentiation2 and MOA
```{r}
diffmoasum <- dat %>% group_by(MOA, differentiation2) %>% 
  summarise(n = length(differentiation2))

```

```{r}
moa_diff <- diffmoasum %>% 
  ggplot(aes(x = MOA, y = n, fill = differentiation2)) +
  geom_bar(stat = "identity", size = 0) +
   scale_fill_manual(values = pal[c(2,5)], 
                    guide = guide_legend(nrow = 4, title = "Differentiation capacity"),
                    labels = c("Not demonstrated", "Demonstrated")) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure 10. TOP") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                   angle = -60, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"),
        legend.title = element_text(size = 8))
ggsave("figs/fig_10_moa_diff.tif", 
       plot = moa_diff, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
res <- table(dat$differentiation2, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
chisq.test(table(dat$differentiation2, dat$MOA))$exp;table(dat$differentiation2, dat$MOA)
test_anno <- paste0("There is  significant association between MOA and demonstration of differentiation capacity(", res$method, ": p = ", round(res$p.value, 3),") with more studies demonstrating differentiation for Immune MOA, and fewer for Paracrine and Multiple MOA than expected.")
```

```{r moa-potency-prep}
moa_potency_summary <- dat %>% 
  group_by(potency, MOA) %>% 
  summarise(n = length(MOA))
```

```{r moa_potency}
moa_potency <- moa_potency_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = potency)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 5, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 5),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  labs(title = "Wilson, Alison, Figure x2. TOP") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        plot.caption = element_text(size = 4, hjust = 0),
        legend.position = c(0.7, 0.8),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))
ggsave("figs/fig_x2_moa_potency.tif", 
       plot = moa_potency, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)
```

```{r}
cd_dat_summary <- cd_dat %>% 
  group_by(Ref, marker) %>% 
  summarise(mean_value = mean(value),
            n = length(value),
            se_value = sd(value)/sqrt(n))
str(cd_dat_summary)
# length(unique(cd_dat$marker)) *length(unique(cd_dat$Ref))

# bind the range and the sinlge value dataframes
cd_dat_summary <- rbind(data.frame(cd_dat_summary), cd_dat2)

```

```{r}
# count the number of refs that have values
cd_refs_by_marker <- cd_dat_summary %>% 
  group_by(marker) %>%
  summarise(n_refs = length(mean_value[!is.na(mean_value)]))

cd_refs_by_marker$marker
isct <- c("Viability","CD73", "CD90", "CD105", "CD34", "CD45" , "CD11b", "CD14" , "CD79α", "CD19", "HLA-DR")
cd_refs_by_marker$ISCT <- "Other marker"
cd_refs_by_marker$ISCT[cd_refs_by_marker$marker %in% isct] <- "ISCT phenotype marker"

cd_refs_by_marker$ISCT <- fct_relevel(cd_refs_by_marker$ISCT,
                              "ISCT phenotype marker",
                              "Other marker")

```

```{r cd-refs-bar}
cd_refs_bar <- cd_refs_by_marker %>% 
  arrange(ISCT, n_refs) %>%
         mutate(marker = factor(marker, levels = marker) ) %>% 
  ggplot(aes(x = reorder(marker, ISCT), y = n_refs, fill = ISCT )) +
  geom_bar(stat = "identity",  size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 15, 1),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 15),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_manual(values = pal[c(5, 2)], 
                    name = NULL) +
  labs(title = "Wilson, Alison, Figure X3. TOP" ) +
  annotate("segment", x = 0.5, xend = 10.5, 
           y = 14, yend = 14,
           colour = "black", size = 1) +
  annotate("segment", x = 0.58, xend = 0.58, 
           y = 14, yend = 13.5,
           colour = "black", size = 1) +
  annotate("segment", x = 10.38, xend = 10.38, 
           y = 14, yend = 13.5,
           colour = "black", size = 1) +
  annotate("text", x = 3,  y = 10, 
           label = "ISCT phenotype\nmarker", size = 4) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

ggsave("figs/fig_x3_cd_refs_bar.tif", 
       plot = cd_refs_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}

cd_dat_summary_values <- cd_dat_summary %>% 
  filter(!is.na(mean_value))

cd_dat_summary_values$ISCT <- "Other marker"
cd_dat_summary_values$ISCT[cd_dat_summary_values$marker %in% isct] <- "ISCT phenotype marker"

cd_dat_summary_values$ISCT <- fct_relevel(cd_dat_summary_values$ISCT,
                              "ISCT phenotype marker",
                              "Other marker")
```

```{r}
cd_values_point_isct <- cd_dat_summary_values %>% 
  filter(ISCT == "ISCT phenotype marker") %>% 
  ggplot(aes(x = marker, y = mean_value)) +
  geom_pointrange(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                  position = position_jitter(width = 0.5), shape = 20) +
  xlab("") +
  scale_y_continuous(name = "Value reported", 
                     breaks = seq(0, 110, 10),
                     minor_breaks = seq(0, 110, 10),
                     limits = c(0, 110),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure X4. TOP" ) +
  geom_vline(xintercept = seq(1.5, 10.5, 1), linetype = "longdash") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4))
ggsave("figs/fig_x4_cd_values_isct.tif", 
       plot = cd_values_point_isct, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

```{r}
cd_values_point_other <- cd_dat_summary_values %>% 
  filter(ISCT == "Other marker") %>% 
  ggplot(aes(x = marker, y = mean_value)) +
  geom_pointrange(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                  position = position_jitter(width = 0.5), shape = 20) +
  xlab("") +
  scale_y_continuous(name = "Value reported", 
                     breaks = seq(0, 110, 10),
                     minor_breaks = seq(0, 110, 10),
                     limits = c(0, 110),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure X4. TOP" ) +
  geom_vline(xintercept = seq(1.5, 10.5, 1), linetype = "longdash") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        # legend.title = element_text(size = 8, colour = "black"),
        # legend.text = element_text(size = 8, colour = "black"),
        # legend.key.size = unit(0.2, "in"),
        # legend.position = c(0.7, 0.8),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4))
ggsave("figs/fig_x5_cd_values_isct.tif", 
       plot = cd_values_point_other, 
       device = device,
       width = fig_w_1.5, 
       height = fig_w,
       units = units,
       dpi = dpi)

```

### 2020-04-19 paper2_figures_viridis_checked.Rmd
fig 8 added

@@
 
+```{r}
+dat %>% group_by(other_functionality) %>% 
+  summarise(n = length(other_functionality), pc = n/84)
+```
 # Figures
@@
            stat = "identity", width = 0.6) +
-  scale_fill_manual(values =  pal[c(1, 2, 5)],
+  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                     name = "Test results",
@@
 
+# Possible alternative to Fig 7 (and 6b)
 ```{r}
@@
             colour = "white")+
-    scale_fill_manual(values =  pal[c(1, 2, 5)],
+    scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                     name = "Test results",
@@
             size = 1, linetype = 1,
-            colour = pal[6], alpha = 0) +
+            colour = "black", alpha = 0) +
   labs(title = "Wilson, Alison, Figure 7ALT. TOP" ) +
@@
 
-ggsave("figs/fig_7_alt.tif", 
+ggsave("figs/fig_7_charact_by_marker_ALTERNATIVE.tif", 
        plot = fig7alt, 
@@
 # Figure 8
+```{r}
+functionality <- dat %>% 
+  select(O, A, C, other_functionality) %>% 
+  pivot_longer(cols = everything(), names_to = "Functionality", values_to = "status") %>% 
+  group_by(Functionality, status) %>% 
+  summarise(n = length(status))
+
+# status
+# recode status
+functionality <- functionality %>%
+  mutate(status = recode_factor(status,
+                                p = "Performed",
+                                m = "Mentioned",
+                                n = "Not mentioned"))
+
+functionality$status <- fct_relevel(functionality$status,
+                                    "Not mentioned",
+                                    "Mentioned",
+                                    "Performed")
+
+# recode functionality
+functionality <- functionality %>%
+  mutate(potency_ass = recode_factor(Functionality,
+                                     other_functionality = "Other functionality",
+                                     C = "Chondrogenesis",
+                                     A = "Adipogenesis",
+                                     O = "Osteogenesis"))
+
+functionality$potency_ass <- fct_relevel(functionality$potency_ass,
+                                         "Other functionality",
+                                         "Chondrogenesis",
+                                         "Adipogenesis",
+                                         "Osteogenesis")
+
+```
+
+```{r}
+fig8 <- functionality %>% 
+  ggplot() +
+  geom_bar(aes(x = potency_ass, y = n, fill = status),
+           stat = "identity", position = position_dodge()) +
+  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
+                    name = "Assessment",
+                    guide = guide_legend(nrow = 2, title.position = "top", title.hjust = 0.5 )) +
+  scale_y_continuous(name = "Number of Articles",
+                     breaks = seq(0, 80, 10),
+                     minor_breaks = seq(0, 80, 10),
+                     limits = c(0, 80),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0.5), name = "Functionality") +
+  labs(title = "Wilson, Alison, Figure 8. TOP" ) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4),
+        legend.position = "top",
+        legend.text = element_text(size = 8, colour = "black"),
+        legend.key.size = unit(0.2, "in")) +
+  coord_flip()
+
+ggsave("figs/fig_8_functionality_assessment.tif", 
+       plot = fig8, 
+       device = device,
+       width = fig_w, 
+       height = fig_w,
+       units = units,
+       dpi = dpi)
+```
 

### 2020-04-27 paper2_figures.Rmd
draft

--- 2020-04-17 paper2_figures_viridis_checked.Rmd
@@
 *  *.tif* or .eps 
-* final publication size; 1-column width or, if necessary, 1½ column width. The * 2-column width should not be used unless necessary.
+* final publication size; 1-column width or, if necessary, 1½ column width. The  2-column width should not be used unless necessary.
 * 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
@@
 * bold enough to be easily read after reduction, as should all symbols used in the * figure.
-Line or bar graphs or flow charts with text should be created in black and * white, not shades of gray, which are difficult to reproduce in even tones.
-If more * than two sets of data are represented, use of fill patterns or colors (not gray) is * suggested to present the data clearly.
-* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for * combination halftones, and 1000 dpi for line art.
+Line or bar graphs or flow charts with text should be created in black and white, not shades of gray, which are difficult to reproduce in even tones.
+If more than two sets of data are represented, use of fill patterns or colors (not gray) is suggested to present the data clearly.
+* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for  combination halftones, and 1000 dpi for line art.
 
@@
 library(tidyverse)
-library(RColorBrewer)
-library(readxl)
-library(kableExtra)
+# library(readxl)
+# library(kableExtra)
 library(tiff)
@@
 library(patchwork)
+library(janitor)
 
@@
 fig_h_1.5 <- 4.5 * 1.5
-dpi <- 300
+dpi <- 600
 device <- "tiff"
@@
 
-```{r import}
-# file <- here::here("data", "Checked Data.xlsx")
-# 
-# # added a row for column names more useful
-# # # skipped first two rows of of old col names
-# 
-# dat <- read_excel(file, sheet = "Checked Data")
-
-```
-
-```{r tidy-data}
-# recode country so those with one paper are
-# "Other"
-# dat <- dat %>%
-#   mutate(Country2 = recode_factor(Country,
-#                                 Brazil = "Brazil",
-#                                 China = "China",
-#                                 Denmark = "Denmark",
-#                                 Egypt = "Egypt",
-#                                 India = "India",
-#                                 Japan = "Japan",
-#                                 Korea = "Korea",
-#                                 Netherlands = "Netherlands",
-#                                 Poland = "Poland",
-#                                 `Rep Korea` = "Rep Korea",
-#                                 Russia = "Russia",
-#                                 Spain = "Spain",
-#                                 Taiwan = "Taiwan",
-#                                 USA = "USA",
-#                                 .default = "Other"))
-```
-
-```{r}
-# dat <- dat %>%
-#   mutate(Phase_condensed = recode_factor(Phase,
-#                                I = "I",
-#                                `I/IIa` = "I",
-#                                `I/II` = "I",
-#                                 II = "II",
-#                                 IIa = "II",
-#                                IIb = "II",
-#                                III = "III"))
-```
-
-```{r}
-# dat <- dat %>%
-#   mutate(test_results = recode_factor(`Test Results?`,
-#                                        n = "Average value (n)",
-#                                        s = "Stated as 'standard phenotype' (s)",
-#                                        o = "Not discussed (o)",
-#                                        y = "Phenotypic markers reported (y)",
-#                                        t = "Tests done but not reported (t)"))
-# dat$test_results <- fct_relevel(dat$test_results,
-#                               "Phenotypic markers reported (y)", 
-#                               "Average value (n)",
-#                               "Tests done but not reported (t)",
-#                               "Stated as 'standard phenotype' (s)",
-#                               "Not discussed (o)")
-```
-
-```{r}
-# MOA - recode NS to Not stated
-# dat <- dat %>%
-#   mutate(MOA = recode_factor(MOA,
-#                              NS = "Not stated",
-#                              paracrine = "Paracrine",
-#                              immune = "Immune",
-#                              differentiation = "Differentiation",
-#                              multi = "Multiple"))
-# 
-# dat$MOA <- fct_relevel(dat$MOA,
-#                        "Paracrine",
-#                        "Immune",
-#                        "Differentiation",
-#                        "Multiple",
-#                        "Not stated")
-```
-
-```{r}
-# recode stem/stromal
-# dat <- dat %>%
-#   mutate(stem_stromal = recode_factor(`Stem/Stromal`,
-#                              `multipotent stromal` = "Multipotent Stromal",
-#                              regenerative = "Regenerative",
-#                              stem = "Stem",
-#                              stromal = "Stromal"))
-# 
-# dat$stem_stromal <- fct_relevel(dat$stem_stromal,
-#                                 "Stromal",
-#                                 "Stem",
-#                                 "Multipotent Stromal",
-#                                 "Regenerative")
-# note: no longer an 'other' category, new regerative category
-```
-
-```{r}
-
-# # Recode O, A and C into the 5 categories that appar 
-# dat <- dat %>%
-#   mutate(differentiation = ifelse(O == "y" &
-#                             A == "y" &
-#                             C == "y",
-#                           "Demonstrated tripotency",
-#                           ifelse(O == "n" &
-#                                    A == "n" &
-#                                    C == "n",
-#                                  "Not Stated",
-#                                  ifelse(O == "y" &
-#                                           A == "y" &
-#                                           C == "n",
-#                                         "Demonstrated bipotency (OA)",
-#                                         ifelse(O == "y" &
-#                                                  A == "n" &
-#                                                  C == "n",
-#                                                "Demonstrated potency (O)",
-#                                                ifelse(O == "m"
-#                                                       & A == "m" &
-#                                                         C == "n",
-#                                                       "Claimed bipotency (OA)",
-#                                                       ifelse(O == "m" &
-#                                                                A == "m" &
-#                                                                C == "m",
-#                                                              "Claimed tripotency", NA)))))))        
-# 
-# dat$differentiation <- fct_relevel(dat$differentiation,
-#                                 "Demonstrated tripotency",
-#                                 "Demonstrated bipotency (OA)",
-#                                 "Demonstrated potency (O)",
-#                                 "Claimed tripotency",
-#                                 "Claimed bipotency (OA)",
-#                                 "Not Stated")                        
-```
-
-```{r}
-# Recode O, A and C into 2 categories, all n = No, anything else = Yes 
-# dat <- dat %>%
-#   mutate(differentiation2 = ifelse(O == "n" &
-#                                    A == "n" &
-#                                    C == "n",
-#                                  "No", "Yes"))      
-# 
-# dat$differentiation2<- fct_relevel(dat$differentiation2,
-#                                 "No","Yes")                        
-```
 ## write to file
 ```{r}
-# file <- "data/checked_processed.csv"
+# file <- "data/checked_processed_aw_corrections.csv"
 # write_csv(dat, file)
@@
 dat <- read_csv(file)
-```
-
-```{r}
-dat <- dat %>%
-  mutate(test_results = recode_factor(`Test Results?`,
-                                       n = "Average value (n)",
-                                       s = "Stated as 'standard phenotype' (s)",
-                                       o = "Not discussed (o)",
-                                       y = "Phenotypic markers reported (y)",
-                                       t = "Tests done but not reported (t)"))
-dat$test_results <- fct_relevel(dat$test_results,
-                              "Phenotypic markers reported (y)",
-                              "Average value (n)",
-                              "Tests done but not reported (t)",
-                              "Stated as 'standard phenotype' (s)",
-                              "Not discussed (o)")
-```
-
-```{r}
-# add a count of the number of markers tested for "Average value (n)". select columns like _test
-test_cols <- names(select(dat, ends_with("_test")) )
-dat <- dat %>%
-  mutate(marker_count = rowSums(.[test_cols] == "p"))
-
-```
-
-```{r}
-
-dat %>% group_by(MOA) %>% summarise(n = length(MOA))
-
-dat$MOA <- fct_relevel(dat$MOA,
-                       "Paracrine",
-                       "Immune",
-                       "Differentiation",
-                       "Multiple",
-                       "Not stated")
-```
-
-```{r}
-dat %>% group_by(stem_stromal) %>% summarise(n = length(stem_stromal))
-
-dat$stem_stromal <- fct_relevel(dat$stem_stromal,
-                                "Stromal",
-                                "Stem",
-                                "Multipotent Stromal",
-                                "Regenerative")
-```
-
-```{r}
-# cd values for
-
-# note: file had missing value for Phas, this was looked up in "Meta-Analysis Data Collection.xlsx"
-# as phase I/IIa
-# note: ref 55, patient 6, marker CD45+/CD105+ contained value ND - I assumed this was no data.
-# note - I have assumed range  is mean +/- se (not sd)
-# file <- here::here("data", "Paper 2 - Charts for Emma.xlsx")
-# cd_dat <- read_excel(file, sheet = "cd_values_single")
-# cd_dat2 <- read_excel(file, sheet = "cd_values_range")
-```
-
-```{r tidy-cd-data}
-# cd_dat <- cd_dat %>% 
-#   gather(key = marker, value = value, -Ref, -Phase, -patient, -notes)
-# cd_dat$value <- as.numeric(cd_dat$value)
-# 
-# cd_dat2 <- cd_dat2 %>% 
-#   gather(key = marker, value = value, -Ref, -Phase, -n)
-# 
-# for (i in 1:length(cd_dat2$value)) {
-#   temp <- strsplit(cd_dat2$value[i], split = "\\s.\\s") %>% unlist()
-#   cd_dat2$mean_value[i] <- as.numeric(temp[1])
-#   cd_dat2$se_value[i] <- as.numeric(temp[2])
-# }
-# cd_dat2 <- cd_dat2 %>% 
-#   filter(!is.na(value)) %>% 
-#   select(Ref, marker, mean_value, n, se_value, -Phase, -value)
-
-```
-
-```{r}
-dat %>% group_by(O) %>% 
-  summarise(n = length(O), pc = n/84)
-```
-```{r}
-dat %>% group_by(A) %>% 
-  summarise(n = length(A), pc = n/84)
-```
-```{r}
-dat %>% group_by(C) %>% 
-  summarise(n = length(C), pc = n/84)
-```
-```{r}
-dat %>% group_by(differentiation) %>% 
-  summarise(n = length(differentiation), pc = n/84)
+# write(names(dat), "data/varnames.txt")
+
+```
+
+```{r}
+# put levels in
+source("levels.R")
 ```
@@
                          1986))
-
-orig$step_names <- fct_relevel(orig$step_names,
-                               "mesenchymal",
-                               "article",
-                               "cell tissue etc",
-                               "clinical etc",
-                               "not biotech etc",
-                               "exc conf etc")
 
@@
             data = labels, 
-            size = 2,
+            size = 3,
             label.size = 0,
@@
         axis.ticks.x = element_blank(),
-        axis.text.y  = element_text(size = 6, colour = "black"),
+        axis.text.y  = element_text(size = 7, colour = "black"),
         panel.grid.major.x = element_blank(),
@@
 summary_country <- dat %>%
-  group_by(Country) %>% 
-  summarise(n = length(Country))
+  group_by(country) %>% 
+  summarise(n = length(country))
 
@@
 country_bar <- summary_country %>% 
-  ggplot(aes(x = reorder(Country, n), y = n)) +
+  ggplot(aes(x = reorder(country, n), y = n)) +
   geom_bar(stat = "identity", fill = pal[3],
@@
   theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(size = 6, colour = "black"),
+        axis.text.x = element_text(size = 7, colour = "black"),
         axis.ticks.y = element_blank(),
-        axis.text.y  = element_text(size = 6, colour = "black"),
+        axis.text.y  = element_text(size = 7, colour = "black"),
         panel.grid.major.x = element_blank(),
@@
 summary_phase <- dat %>%
-  group_by(Phase) %>% 
-  summarise(n = length(Phase),
+  group_by(phase) %>% 
+  summarise(n = length(phase),
             pc = paste0(round(100 * n / 84, 1 ), "%"))
-summary_phase <- summary_phase %>%
-  mutate(Phase_condensed = recode_factor(Phase,
-                               I = "I",
-                               `I/IIa` = "I",
-                               `I/II` = "I",
-                                II = "II",
-                                IIa = "II",
-                               IIb = "II",
-                               III = "III",
-                               NS = "NS"))
 
 summary_phase_condensed <- dat %>%
-  group_by(Phase_condensed) %>% 
-  summarise(n = length(Phase_condensed),
+  group_by(phase_condensed) %>% 
+  summarise(n = length(phase_condensed),
             pc = paste0(round(100 * n / 84, 1 ), "%"))
@@
 phase_bar <- summary_phase %>% 
-  ggplot(aes(x = reorder(Phase,n), y = n)) +
+  ggplot(aes(x = reorder(phase,n), y = n)) +
   geom_bar(stat = "identity", fill = pal[3], size = 0) +
@@
 
-### Three phase
-
-```{r fig4-phase-3}
-# phase_3_bar <- summary_phase_condensed %>% 
-#   ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
-#   geom_bar(stat = "identity", fill = pal[3],size = 0) +
-#   xlab("") +
-#   geom_text(aes(y = n + 6, label = pc) ) +
-#   scale_y_continuous(name = "Number of Articles", 
-#                      breaks = seq(0, 65, 5),
-#                      minor_breaks = seq(0, 65, 1),
-#                      limits = c(0, 65),
-#                      expand = c(0, 0)) +
-#   scale_x_discrete(expand = c(0, 0)) +
-#   labs(title = "Wilson, Alison, Figure 4. TOP" ) +
-#   theme_classic() +
-#   theme(axis.title.y = element_blank(),
-#         axis.text.x = element_text(size = 8, colour = "black"),
-#         axis.ticks.y = element_blank(),
-#         axis.text.y  = element_text(size = 8, colour = "black"),
-#         panel.grid.major.x = element_blank(),
-#         panel.grid.minor.x = element_blank(),
-#         panel.grid.minor.y = element_blank(),
-#         plot.title = element_text(hjust = 0, size = 4)) +
-#   coord_flip()
-# 
-# ggsave("figs/fig_4_Article_phase_3.tif", 
-#        plot = phase_3_bar, 
-#        device = device,
-#        width = fig_w, 
-#        height = fig_w,
-#        units = units,
-#        dpi = dpi)
-
-```
-
 ## Figure 5 Articles by Source-Year
@@
 summary_tissue <- dat %>% 
-  group_by(Source, Year = factor(Year), 
+  group_by(source, year, 
            .drop = FALSE) %>% 
-  summarise(n = length(Source))
+  summarise(n = length(source))
 dat %>% 
-  group_by(Source, 
+  group_by(source, 
            .drop = FALSE) %>% 
-  summarise(n =length(Source), pc = n/84)
+  summarise(n =length(source), pc = n/84)
 
@@
 source_year <- summary_tissue %>% 
-  ggplot(aes(x = Year, y = n, fill = Source)) +
+  ggplot(aes(x = year, y = n, fill = source)) +
   geom_bar(stat = "identity", size = 0) +
@@
 summary_test <- dat %>% 
-  group_by(test_results) %>% 
-  summarise(n = length(test_results),
+  group_by(test_results_2) %>% 
+  summarise(n = length(test_results_2),
             pc = paste0(round(100 * n / 84, 1 ), "%"))
@@
 test_bar <- summary_test %>% 
-  ggplot(aes(x = reorder(test_results, n), y = n, fill = test_results)) +
+  ggplot(aes(x = reorder(test_results_2, n), y = n, fill = test_results_2)) +
   geom_bar(stat = "identity", size = 0) +
@@
 ```{r}
+dat %>% 
+  filter(test_results_2 != "Average value (n)") %>%
+  filter(marker_count == 1) %>% 
+  select(ref_number,test_results_2, test_results)
+
 summary_marker_count <- dat %>% 
-  filter(test_results == "Average value (n)") %>%
+  filter(test_results_2 == "Average value (n)") %>%
   group_by(marker_count) %>% 
@@
 dat %>%
-  group_by(Phase_condensed) %>% 
-  summarise(n = length(Phase_condensed),
+  group_by(phase_condensed) %>% 
+  summarise(n = length(phase_condensed),
             pc = n/84)
@@
 summary_phase_test <- dat %>%
-  group_by(Phase_condensed, test_results) %>% 
-  summarise(n = length(Phase_condensed))
+  group_by(phase_condensed, test_results_2) %>% 
+  summarise(n = length(phase_condensed))
 ```
@@
 phase_test <- summary_phase_test %>% 
-  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
+  ggplot(aes(x = phase_condensed, y = n, fill = test_results_2)) +
   geom_bar(stat = "identity", size = 0) +
@@
 
-### Stacked by percent of article
-
-```{r fig7-phase-test-pc}
-# phase_test2 <- summary_phase_test %>% 
-#   ggplot(aes(x = Phase_condensed, y = n)) +
-#   geom_bar(aes(fill = test_results), 
-#            stat = "identity", 
-#            size = 0, 
-#            position = "fill") +
-#   scale_fill_manual(values = pal,
-#                     name = "Test results") +
-#   scale_y_continuous(name = "Proportion of Articles",
-#                      breaks = seq(0, 1, 0.2),
-#                 #     limits = c(0, 1.2),
-#                      expand = c(0, 0)) +
-#   scale_x_discrete(expand = c(0, 0), name = "Phase") +
-#   geom_text(data = summary_phase_condensed,
-#             aes(x = Phase_condensed, y = 1.05, vjust = 1,
-#                 label = paste("n = ",n)),size=3) +
-#  labs(subtitle = "B") +
-#   theme_classic() +
-#   theme(axis.text.x = element_text(size = 8, colour = "black"),
-#         axis.text.y  = element_text(size = 8, colour = "black"),
-#         panel.grid.major.x = element_blank(),
-#         panel.grid.minor.x = element_blank(),
-#         panel.grid.minor.y = element_blank(),
-#         #  plot.title = element_text(hjust = 0, size = 8),
-#         legend.position = "none",
-#         plot.margin = margin(r = 0, l = 0, unit="in"))
-
-```
-
 ```{r fig6}
@@
 layout <- "
-aaaaaaa#
-aaaaaaa#
-aaaaaaa#
-#bbbbccc
-#bbbbccc
-#bbbbccc
-#bbbbccc
-#bbbbccc
+aa
+bc
 "
@@
 
-```{r}
-dat
-```
-
 ## Figure 7 Characterisation by marker.
@@
 # select the test columns and count the number of articles for each marker and category
-test_cols
-
-charact_by_marker_ref <- dat %>% 
-  select(ends_with("_test"), `Ref #`) %>% 
-  pivot_longer(cols = -`Ref #`, names_to = "marker", values_to = "status")
+test_cols <- names(select(dat, ends_with("_test")))
+
+test_by_attribute <- dat %>% 
+  select(test_cols, ref_number) %>% 
+  pivot_longer(cols = -ref_number, 
+               names_to = "marker", 
+               values_to = "status")
 
@@
 
-charact_by_marker_ref <- charact_by_marker_ref %>% 
+test_by_attribute <- test_by_attribute %>% 
   mutate(marker2 = str_replace(marker, "_test", ""))
@@
 # set the levels in that order
-charact_by_marker_ref$marker2 <- factor(charact_by_marker_ref$marker2, levels = test_cols)
+test_by_attribute$marker2 <- factor(charact_by_marker_ref$marker2, 
+                                    levels = test_cols)
 
@@
 # recode status
-charact_by_marker_ref <- charact_by_marker_ref %>%
+test_by_attribute <- test_by_attribute %>%
   mutate(test_status = recode_factor(status,
@@
 
-charact_by_marker_ref$test_status <- fct_relevel(charact_by_marker_ref$test_status,
+test_by_attribute$test_status <- fct_relevel(test_by_attribute$test_status,
                                              "Not mentioned",
@@
 
-charact_by_marker_summary <- charact_by_marker_ref %>% 
+test_by_attribute_summary <- test_by_attribute %>% 
   group_by(marker2, test_status) %>% 
@@
 ```{r}
-fig7 <- charact_by_marker_summary %>% 
+fig7 <- test_by_attribute_summary %>% 
   ggplot() +
@@
   theme_classic() +
-  theme(axis.text.x = element_text(size = 6, colour = "black",
-                                   angle = -60, hjust = 0),
+  theme(axis.text.x = element_text(size = 6, colour = "black"),
         axis.text.y  = element_text(size = 8, colour = "black"),
@@
         legend.text = element_text(size = 8, colour = "black"),
-        legend.key.size = unit(0.2, "in"))
+        legend.key.size = unit(0.2, "in")) +
+  coord_flip()
 
@@
 
+# Possible alternative to Fig 7 (and 6b)
 ```{r}
 #alt fig
-fig7alt <- charact_by_marker_ref %>% 
+fig7alt <- test_by_attribute %>% 
   ggplot() +
-  geom_tile(aes(x = factor(`Ref #`), y = marker2 , fill = test_status),
+  geom_tile(aes(x = factor(ref_number), y = marker2 , fill = test_status),
             colour = "white")+
-    scale_fill_manual(values =  pal[c(1, 2, 5)],
+    scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
                     name = "Test results",
@@
 # Figure 8
+```{r}
+functionality <- dat %>% 
+  select(O, A, C, other_functionality) %>% 
+  pivot_longer(cols = everything(), names_to = "type", values_to = "status") %>% 
+  group_by(type, status) %>% 
+  summarise(n = length(status)) %>% 
+  ungroup(type, status)
+
+# status
+# recode status
+functionality <- functionality %>%
+  mutate(status = recode_factor(status,
+                                p = "Performed",
+                                m = "Mentioned",
+                                n = "Not mentioned"))
+
+functionality$status <- fct_relevel(functionality$status,
+                                    "Not mentioned",
+                                    "Mentioned",
+                                    "Performed")
+levels(functionality$status)
+
+# recode functionality
+functionality <- functionality %>%
+  mutate(type = recode_factor(type,
+                              other_functionality = "Other functionality",
+                              C = "Chondrogenesis",
+                              A = "Adipogenesis",
+                              O = "Osteogenesis"))
+
+functionality$type <- fct_relevel(functionality$type,
+                                         "Other functionality",
+                                         "Chondrogenesis",
+                                         "Adipogenesis",
+                                         "Osteogenesis")
+
+```
+
+```{r}
+fig8 <- functionality %>% 
+  ggplot() +
+  geom_bar(aes(x = type, y = n, fill = status),
+           stat = "identity", position = position_dodge()) +
+  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
+                    name = "Assessment",
+                    guide = guide_legend(nrow = 2, title.position = "top", title.hjust = 0.5 )) +
+  scale_y_continuous(name = "Number of Articles",
+                     breaks = seq(0, 80, 10),
+                     minor_breaks = seq(0, 80, 10),
+                     limits = c(0, 80),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0.5), name = "Functionality") +
+  labs(title = "Wilson, Alison, Figure 8. TOP" ) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4),
+        legend.position = "top",
+        legend.text = element_text(size = 8, colour = "black"),
+        legend.key.size = unit(0.2, "in")) +
+  coord_flip()
+
+ggsave("figs/fig_8_functionality_assessment.tif", 
+       plot = fig8, 
+       device = device,
+       width = fig_w, 
+       height = fig_w,
+       units = units,
+       dpi = dpi)
+```
 
@@
 ```{r}
-diffmoasum <- dat %>% group_by(MOA, differentiation2) %>% 
-  summarise(n = length(differentiation2))
+diffmoasum <- dat %>% group_by(MOA, differentiation_2) %>% 
+  summarise(n = length(differentiation_2))
 
@@
 moa_diff <- diffmoasum %>% 
-  ggplot(aes(x = MOA, y = n, fill = differentiation2)) +
+  ggplot(aes(x = MOA, y = n, fill = differentiation_2)) +
   geom_bar(stat = "identity", size = 0) +
@@
 ```{r}
-res <- table(dat$differentiation2, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
-chisq.test(table(dat$differentiation2, dat$MOA))$exp;table(dat$differentiation2, dat$MOA)
+res <- table(dat$differentiation_2, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
+chisq.test(table(dat$differentiation_2, dat$MOA))$exp;table(dat$differentiation_2, dat$MOA)
 test_anno <- paste0("There is  significant association between MOA and demonstration of differentiation capacity(", res$method, ": p = ", round(res$p.value, 3),") with more studies demonstrating differentiation for Immune MOA, and fewer for Paracrine and Multiple MOA than expected.")
 ```
-
-```{r moa-potency-prep}
-moa_potency_summary <- dat %>% 
-  group_by(potency, MOA) %>% 
-  summarise(n = length(MOA))
-```
-
-```{r moa_potency}
-moa_potency <- moa_potency_summary %>% 
-  ggplot(aes(x = MOA, y = n, fill = potency)) +
-  geom_bar(stat = "identity", size = 0) +
-  scale_fill_manual(values = pal, 
-                    guide = guide_legend(nrow = 5, title = NULL)) +
-  scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 45, 5),
-                     minor_breaks = seq(0, 45, 5),
-                     limits = c(0, 45),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
-  labs(title = "Wilson, Alison, Figure x2. TOP") +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black"),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        plot.caption = element_text(size = 4, hjust = 0),
-        legend.position = c(0.7, 0.8),
-        legend.text = element_text(size = 6, colour = "black"),
-        legend.key.size = unit(0.2, "in"))
-ggsave("figs/fig_x2_moa_potency.tif", 
-       plot = moa_potency, 
-       device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-```
+# CD values figures
 
@@
 ```
+
+```{r}
+
+# disease targets
+dat %>% group_by(Indication) %>% 
+  summarise(n = length(Indication)) %>% 
+  ggplot(aes(x = Indication, y = n)) +
+  geom_bar(stat="identity")
+
+```

### 2020-04-27 levels.R

@@ -1,0 +1,31 @@
+# levelling factors
+dat$test_results_2 <- fct_relevel(dat$test_results_2,
+                                "Phenotypic markers reported (y)",
+                                "Average value (n)",
+                                "Tests done but not reported (t)",
+                                "Stated as 'standard phenotype' (s)",
+                                "Not discussed (o)")
+dat$MOA <- fct_relevel(dat$MOA,
+                       "Paracrine",
+                       "Immune",
+                       "Differentiation",
+                       "Multiple",
+                       "Not stated")
+
+dat$stem_stromal <- fct_relevel(dat$stem_stromal,
+                                "Stromal",
+                                "Stem",
+                                "Multipotent Stromal",
+                                "Regenerative")
+
+dat$funding <- fct_relevel(dat$funding,
+                           "Commercial",
+                           "National government",
+                           "Regional government",
+                           "Other grant",
+                           "Mix",
+                           "None",
+                           "Not stated")
+
+# turn year into a factor
+dat$year <- factor(dat$year)

### 2020-05-17 scripts/working.R
HDI and JIF added to dataset

@@ -1,96 +1,40 @@
-stages <- tibble(
-  clicks = 1,
-  signups = .47,
-  cart = .09,
-  buys = .05
-) %>%
-  gather(stage, percent)
-
-stages
-to_poly <- stages %>%
-  arrange(percent) %>%
-  mutate(
-    group = row_number(),
-    x1 = 0 + ((1 - percent)/2),
-    x4 = percent + ((1 - percent)/2),
-    x2 = lag(x1), 
-    x3 = lag(x4)
-  ) %>%
-  mutate(
-    x2 = ifelse(is.na(x2), x1, x2),
-    x3 = ifelse(is.na(x3), x4, x3)
-  ) %>%
-  gather(key = xpoint, value = x, -stage,-group, -percent) %>%
-  arrange(group, xpoint) %>%
-  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))
-
-to_poly
-
-#########################
-orig <- data.frame(step_names = c("mesenchymal",
-                                  "article",
-                                  "cell tissue etc",
-                                  "clinical etc",
-                                  "not biotech etc"),
-                   n = c(65706,
-                         47031,
-                         7814,
-                         5502,
-                         2055))
-
-orig$step_names <- fct_relevel(orig$step_names,
-                               "mesenchymal",
-                               "article",
-                               "cell tissue etc",
-                               "clinical etc",
-                               "not biotech etc")
-# prep polygons that connect
-to_poly_orig <- orig %>%
-  arrange(n) %>%
-  mutate(
-    group = row_number(),
-    x1 = 0 + ((1 - n)/2),
-    x4 = n + ((1 - n)/2),
-    x2 = lag(x1), 
-    x3 = lag(x4)) %>%
-  mutate(
-    x2 = ifelse(is.na(x2), x1, x2),
-    x3 = ifelse(is.na(x3), x4, x3)
-  ) %>%
-  gather(xpoint, x, -step_names,-group, -n) %>%
-  arrange(group, xpoint) %>%
-  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))
+library(tidyverse)
+library(janitor)
 
 
-# EXAMPLE
-# Create the placement of the stages in the plot,
-#  by just adding a 0.5 to each row number
+file <- "data/checked_processed_aw_corrections.csv"
+dat <- read_csv(file, skip = 1) 
 
[…]

### 2020-06-04 paper2_figures.Rmd
HDI and JIF added to dataset
figures 1 - 6 complete

@@
   html_document: default
-  pdf_document: default
+  svg_document: default
 ---
@@
 * Figures may be submitted as multipart panels.
-*  *.tif* or .eps 
+*  *.svg* or .eps 
 * final publication size; 1-column width or, if necessary, 1½ column width. The  2-column width should not be used unless necessary.
@@
 # library(kableExtra)
-library(tiff)
 library(grid)
@@
 units = "in"
-fig_w <- 3.2
-fig_w_1.5 <- 4.5
-fig_w_2 <- 5.8
-fig_h <- 4.5
-fig_h_1.5 <- 4.5 * 1.5
-dpi <- 600
-device <- "tiff"
+fig_w <- 3.5
+fig_w_1.5 <- 5
+fig_w_2 <- 7.3
+fig_h <- fig_w
+device <- "svg"
 
@@
 file <- "data/checked_processed_aw_corrections.csv"
-dat <- read_csv(file)
+dat <- read_csv(file, skip = 1)
 # write(names(dat), "data/varnames.txt")
@@
 
-## Fig 1 - Article search funnel
+## Fig 1 - Search
+
+### prep
 
 ```{r data-prep-fig1}
-# create data
+# create data for funnel 1A
 # short names for proof of method
@@
 # modify the labels
-labels$step_names2 <- c( "EXCLUDE conference proceedings,\nretracted papers",
-                         "EXCLUDE CATEGORIES (NOT\nbiotechnology applied microbiology oncology\nhaematology, engineering biomedical)",
-                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative medicine)",
+labels$step_names2 <- c( "EXCLUDE,\nconference proceedings,\nretracted papers",
+                         "EXCLUDE CATEGORIES (NOT\nbiotechnology, applied\nmicrobiology, oncology\nhaematology,\nengineering biomedical)",
+                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative,\nmedicine)",
                          "REFINE BY CATEGORY\ncell tissue engineering\nand transplantation",
-                         "REFINE BY DOCUMENT TYPE\narticle",
-                         "mesenchymal stem cells OR\nmesenchymal stromal cells OR\nMSC AND characterisation AND clinical")
-```
-
+                         "REFINE BY DOCUMENT\nTYPE article",
+                         "mesenchymal stem cells OR\nmesenchymal stromal cells\nOR MSC AND characterisation,\nAND clinical")
+
+# read data for 1B
+fig1b <- read.table("data/fig1b.txt", header = TRUE)
+
+```
+
+### each panel of fig 1
 ```{r fig1}
+# figure 1 a
 article_funnel <- to_poly_orig %>%
@@
                      labels = labels$step_names2) +
-  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
   theme_minimal() +
@@
         axis.ticks.x = element_blank(),
-        axis.text.y  = element_text(size = 7, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4)) +
+        axis.text.y  = element_text(size = 7, colour = "black", hjust = 0, face = "plain"),
+        panel.spacing = unit(0, "lines"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank()) +
     scale_fill_manual(values = rev(pal))
 
-ggsave("figs/fig_1_Article_search_funnel.tif", 
-       plot = article_funnel, 
+# fig 1b
+
+data_collection <- fig1b %>% 
+  ggplot() +
+  geom_text(aes(x = x, y = y, label = item),
+            size = 2.5,nudge_y = 0.1,
+            hjust = "left") +
+  facet_grid(. ~ data_element) +
+  scale_x_continuous(limits = c(0, 7)) +
+  theme_minimal() +
+  theme(legend.position = "none",
+        strip.text = element_text(hjust = 0, size = 5.5, colour = "white", face = "bold"),
+        strip.background = element_rect(fill = pal[1], colour = pal[1], size = 0.05),
+        panel.border = element_rect(colour = "black", fill = NA),
+        panel.spacing = unit(0, "lines"),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+```
+
+### whole fig 1
+```{r fig1}
+
+layout <- "
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+#aaaaaaaaaaaaaaaaaaa
+bbbbbbbbbbbbbbbbbbbb
+bbbbbbbbbbbbbbbbbbbb
+bbbbbbbbbbbbbbbbbbbb
+"
+
+fig1 <- article_funnel + data_collection + 
+  plot_layout(design = layout) +
+  plot_annotation(tag_levels = "A")&
+    theme(plot.tag = element_text(size = 9, hjust = 1, face = "bold"))
+
+ggsave("figs/fig_1.svg", 
+       plot = fig1, 
        device = device,
        width = fig_w, 
-       height = 3.0,
-       units = units,
-       dpi = dpi)
-```
-
-## Figure 3 Articles by country
-
-```{r country-prep}
+       height = fig_h*1.6,
+       units = units)
+
+```
+
+## Fig 2 - Articles by country, phase, indications, route of admin
+
+### prep
+
+```{r fig2-prep}
+# by country A
 summary_country <- dat %>%
@@
 
-```
-
-```{r fig3-country-bar}
-country_bar <- summary_country %>% 
-  ggplot(aes(x = reorder(country, n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[3],
-           size = 0) +
-  xlab("") +
-  scale_y_continuous(name = "Number of articles", 
-                     breaks = seq(0, 16, 1),
-                     minor_breaks = seq(0, 16, 1),
-                     limits = c(0, 16),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0)) +
-  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
-  theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(size = 7, colour = "black"),
-        axis.ticks.y = element_blank(),
-        axis.text.y  = element_text(size = 7, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4)) +
-  coord_flip()
-ggsave("figs/fig_3_Article_country.tif", 
-       plot = country_bar, 
-       device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-
-```
-## Figure 4 Articles by Phase
-
-### Eight phase version
-
-```{r phase-prep}
-
+# phase B
 summary_phase <- dat %>%
@@
 
-```
-
-```{r fig4-phase}
-phase_bar <- summary_phase %>% 
-  ggplot(aes(x = reorder(phase,n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[3], size = 0) +
+# indication C
+summary_indication <- dat %>%
+  group_by(indication) %>% 
+  summarise(n = length(indication),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+
+# route D
+summary_route <- dat %>%
+  group_by(route) %>% 
+  summarise(n = length(route),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+
+```
+
+### each panel figure 2
+```{r fig2}
+#by country
+country_bar <- summary_country %>% 
+  ggplot(aes(x = reorder(country, n), y = n)) +
+  geom_bar(stat = "identity", fill = pal[4],
+           size = 0, width = 0.8) +
   xlab("") +
-  geom_text(aes(y = n + 4, label = pc) ) +
-  scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 45, 5),
-                     minor_breaks = seq(0, 45, 1),
-                     limits = c(0, 45),
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 15, 5),
+                     minor_breaks = seq(0, 15, 1),
+                     limits = c(0, 16),
                      expand = c(0, 0)) +
   scale_x_discrete(expand = c(0, 0)) +
-  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
   theme_classic() +
@@
 
-ggsave("figs/fig_4_Article_phase.tif", 
-       plot = phase_bar, 
+# by phase
+phase_bar <- summary_phase %>% 
+  ggplot(aes(x = reorder(phase,n), y = n)) +
+  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  xlab("") +
+ # geom_text(aes(y = n + 4, label = pc) ) +
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 35, 10),
+                     minor_breaks = seq(0, 35, 1),
+                     limits = c(0, 35),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.text.x = element_text(size = 8, colour = "black"),
+        axis.ticks.y = element_blank(),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4)) +
+  coord_flip()
+
+# by indication
+indication_bar <- summary_indication %>% 
+  ggplot(aes(x = reorder(indication, n), y = n)) +
+  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  xlab("") +
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 12, 2),
+                     minor_breaks = seq(0, 12, 2),
+                     limits = c(0, 13),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.text.x = element_text(size = 8, colour = "black"),
+        axis.ticks.y = element_blank(),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4)) +
+  coord_flip()
+
+# by route
+route_bar <- summary_route %>% 
+  ggplot(aes(x = reorder(route, n), y = n)) +
+  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  xlab("") +
+#  geom_text(aes(y = n + 3, label = pc) ) +
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 25, 5),
+                     minor_breaks = seq(0, 25, 1),
+                     limits = c(0, 25),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.text.x = element_text(size = 8, colour = "black"),
+        axis.ticks.y = element_blank(),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4)) +
+  coord_flip()
+
+```
+
+### whole fig 2
+```{r fig2-layout}
+
+layout <- "
+a#
+a#
+ad
+ad
+ad
+ad
+ad
+bd
+bd
+bd
+bd
+cd
+cd
+cd
+"
+
+fig2 <- country_bar  + route_bar+ phase_bar+ indication_bar +
+  plot_layout(design = layout) +
+  plot_annotation(caption = "Number of Articles",
+                  tag_levels = "A")&
+    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
+          plot.caption = element_text(size = 9, hjust = 0.5, face = "plain"))
+
+ggsave("figs/fig_2.svg", 
+       plot = fig2, 
        device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-
-```
-
-## Figure 5 Articles by Source-Year
-
-```{r source_year_prep}
-summary_tissue <- dat %>% 
-  group_by(source, year, 
-           .drop = FALSE) %>% 
-  summarise(n = length(source))
-dat %>% 
-  group_by(source, 
-           .drop = FALSE) %>% 
-  summarise(n =length(source), pc = n/84)
-
-```
-
-### stacked
-```{r fig5-source-year-stack}
-source_year <- summary_tissue %>% 
-  ggplot(aes(x = year, y = n, fill = source)) +
-  geom_bar(stat = "identity", size = 0) +
-  scale_fill_manual(values = pal[c(1,3,5,6)],
-                    guide = guide_legend(nrow = 3, title = NULL )) +
+       width = fig_w_2, 
+       height = fig_h*2,
+       units = units)
+
+```
+
+## Fig 3 - Articles by sources, allo/auto stem/stromal
+
+### prep
+
+```{r fig3_prep}
+# source 3a
+summary_source <- dat %>% 
+  group_by(source) %>% 
+  summarise(n = length(source),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+
+# allo va auto 3b
+summary_allo_auto <- dat %>% 
+  group_by(allo_auto) %>% 
+  summarise(n = length(allo_auto),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+
+# stem vs stromal 3b
+summary_stem_stromal <- dat %>% 
+  group_by(stem_stromal) %>% 
+  summarise(n = length(stem_stromal),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+```
+### each panel figure 2
+
+```{r fig_3}
+# source
+source_bar <- summary_source %>% 
+  ggplot(aes(x = source, y = n)) +
+  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
   scale_y_continuous(name = "Number of Articles",
-                    breaks = seq(0, 20, 2),
-                    minor_breaks = seq(0, 20, 2),
-                    limits = c(0, 20),
-                    expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0), name = "Year") +
-  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black"),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        legend.position = c(0.2, 0.9),
-        legend.text = element_text(size = 6, colour = "black"),
-        legend.key.size = unit(0.2, "in"))
-
-ggsave("figs/fig_5_Article_source_year_stack.tif", 
-       plot = source_year, 
+                    breaks = seq(0, 50, 10),
+                    minor_breaks = seq(0, 50, 10),
+                    limits = c(0, 60),
+                    expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = NULL) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black",
+                                  angle = 285, vjust = 0.5, hjust = 0),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+# allo - auto
+allo_auto_bar <- summary_allo_auto %>% 
+  ggplot(aes(x = allo_auto, y = n)) +
+  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
+  scale_y_continuous(name = NULL,
+                    breaks = seq(0, 50, 10),
+                    minor_breaks = seq(0, 50, 10),
+                    limits = c(0, 60),
+                    expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = NULL) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black", 
+                                  angle = 285, vjust = 0.5, hjust = 0),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+# stem_stomal
+stem_stromal_bar <- summary_stem_stromal %>%
+  ggplot(aes(x = stem_stromal, y = n)) +
+  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
+  scale_y_continuous(name = NULL,
+                    breaks = seq(0, 50, 10),
+                    minor_breaks = seq(0, 50, 10),
+                    limits = c(0, 60),
+                    expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = NULL) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black", 
+                                   angle = 285, vjust = 0.5, hjust = 0),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank())
+```
+
+### whole fig 3
+```{r fig_3-layout}
+layout <- "
+aaabbbcccc
+"
+
+fig3 <- source_bar  + allo_auto_bar+ stem_stromal_bar +
+  plot_layout(design = layout) +
+  plot_annotation(caption = "Source",
+                  tag_levels = "A")&
+    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
+          plot.caption = element_text(size = 9, hjust = 0.5, vjust = 1, face = "plain"))
+
+ggsave("figs/fig_3.svg", 
+       plot = fig3, 
        device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-
-```
-
-## Figure 6 - three panels
-
-### panel 1: Articles by Test quality
-
-```{r test-quality-prep}
+       width = fig_w_1.5, 
+       height = fig_h,
+       units = units)
+```
+
+## Fig 4 - characterisation by article
+
+### prep
+
+```{r fig4_prep}
+# test stringency
 summary_test <- dat %>% 
-  group_by(test_results_2) %>% 
-  summarise(n = length(test_results_2),
+  group_by(test_results) %>% 
+  summarise(n = length(test_results),
             pc = paste0(round(100 * n / 84, 1 ), "%"))
-
-```
-
-```{r testquality}
+# phase by stringency
+summary_phase_test <- dat %>%
+  group_by(phase_condensed, test_results) %>% 
+  summarise(n = length(phase_condensed))
+
+# number of markers reported in articles either reporting % by batch of average percentages (p)
+summary_marker_p_count <- dat %>% 
+  filter(test_results != "3. Tests done but % not reported") %>%
+  filter(test_results != "4. Stated as 'standard phenotype'") %>%
+  filter(test_results != "5. No characterisation discussed") %>%
+  group_by(marker_p_count) %>% 
+  summarise(n = length(marker_p_count))
+
+```
+### each panel figure 4
+
+```{r fig_4}
+# test stringency overall
 test_bar <- summary_test %>% 
-  ggplot(aes(x = reorder(test_results_2, n), y = n, fill = test_results_2)) +
+  ggplot(aes(x = test_results, y = n, fill = test_results)) +
   geom_bar(stat = "identity", size = 0) +
   xlab("") +
-  geom_text(aes(y = n + 6, label = pc) ) +
-  scale_fill_manual(values = pal,
+  geom_text(aes(y = n + 6, label = pc), size = 3 ) +
+  scale_fill_manual(values = rev(pal[1:5]),
                     name = "Test results") +
@@
                      minor_breaks = seq(0, 50, 1),
-                     limits = c(0, 50),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0),
-                   labels = c("Stated as 'standard\nphenotype' (s)",
-                              "Phenotypic markers\nreported (y)",
-                              "Tests done but\nnot reported (t)",
-                              "Not discussed (o)",
-                              "Average value (n)")) +
-  labs(subtitle = "A") +
+                     limits = c(0, 53),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), ) +
   theme_classic() +
@@
         panel.grid.minor.y = element_blank(),
-        legend.position = "none",
-        plot.title = element_text(hjust = 0, size = 4),
-        plot.margin = margin(r = 0.1, b = 0.1, l = 0, unit="in")) +
+        legend.position = "none") +
   coord_flip()
 
-# ggsave("figs/fig_6_Article_test_quality.tif", 
-#        plot = test_bar, 
-#        device = device,
-#        width = fig_w, 
-#        height = fig_w,
-#        units = units,
-#        dpi = dpi)
-
-```
-
-### panel 2 how many markers had average values  
-```{r}
-dat %>% 
-  filter(test_results_2 != "Average value (n)") %>%
-  filter(marker_count == 1) %>% 
-  select(ref_number,test_results_2, test_results)
-
-summary_marker_count <- dat %>% 
-  filter(test_results_2 == "Average value (n)") %>%
-  group_by(marker_count) %>% 
-  summarise(n = length(marker_count))
-
-```
-
-```{r markercount}
-marker_bar <- summary_marker_count %>% 
-  ggplot(aes(x = factor(marker_count), y = n)) +
-  geom_bar(stat = "identity", fill = pal[2], size = 0) +
-  scale_y_continuous(name = "Number of\n'Average value (n)' Articles ", 
-                     breaks = seq(0, 12, 2),
-                     minor_breaks = seq(0, 12, 2),
-                     limits = c(0, 12),
-                     expand = c(0, 0)) +
-  scale_x_discrete(name = "Number of markers\nreported by an article",
-                   expand = c(0, 0)) +
-  labs(subtitle = "B") +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black"),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        plot.margin = margin(r = 0.2, t = 0,l = 0, unit="in")) 
-```
-
-### panel 3  Articles by Phase and Test quality reported (previously fig7 a)
-
-### Stacked by number of articles
-```{r}
-
-dat %>%
-  group_by(phase_condensed) %>% 
-  summarise(n = length(phase_condensed),
-            pc = n/84)
-
-summary_phase_test <- dat %>%
-  group_by(phase_condensed, test_results_2) %>% 
-  summarise(n = length(phase_condensed))
-```
-
-```{r phasetest}
+# tests stringency by phase
 phase_test <- summary_phase_test %>% 
-  ggplot(aes(x = phase_condensed, y = n, fill = test_results_2)) +
-  geom_bar(stat = "identity", size = 0) +
+  ggplot(aes(x = phase_condensed, y = n, fill = test_results)) +
+  geom_bar(stat = "identity", size = 0, width = 0.8) +
   scale_fill_manual(values = pal,
-                    name = "Test results") +
+                    name = NULL) +
   scale_y_continuous(name = "Number of Articles",
@@
   scale_x_discrete(expand = c(0, 0), name = "Phase") +
- labs(subtitle = "C") +
   theme_classic() +
@@
         panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 8),
-        legend.position = "none", 
-        plot.margin = margin(r = 0.3, l = 0.1, t = 0, unit="in"))
-
-```
-
-```{r fig6}
-
+        legend.position = "none")
+
+# 
+markerp_bar <- summary_marker_p_count %>% 
+  ggplot(aes(x = marker_p_count, y = n)) +
+  geom_bar(stat = "identity", fill = pal[6], size = 0, width = 0.8) +
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 12, 2),
+                     minor_breaks = seq(0, 12, 2),
+                     limits = c(0, 12),
+                     expand = c(0, 0)) +
+  scale_x_continuous(name = "Number of markers",
+                     breaks = seq(0, 11, 1),
+                    minor_breaks = seq(0, 12, 2),
+                    limits = c(0.5, 12),
+                     expand = c(0, 0)) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+```
+
+### whole fig 4
+```{r fig_4-layout}
 layout <- "
-aa
-bc
+#aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
+bbbcccccccccccccccccccccccccccccccccccc
 "
 
-fig6 <- test_bar + marker_bar + phase_test + 
+layout <- "
+aaaaaabbbcccc
+"
+
+fig4 <- test_bar + phase_test + markerp_bar +
   plot_layout(design = layout) +
-  plot_annotation(title = "Wilson, Alison, Figure 6. TOP")&
-    theme(text = element_text(size = 8, hjust = 0))
-
-ggsave("figs/fig_6.tif", 
-       plot = fig6, 
+  plot_annotation(tag_levels = "A")&
+    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
+
+ggsave("figs/fig_4.svg", 
+       plot = fig4, 
        device = device,
        width = fig_w_2, 
-       height = fig_h,
-       units = units,
-       dpi = dpi)
-
-```
-
-## Figure 7 Characterisation by marker.
+       height = 2.2,
+       units = units)
+```
+
+## Fig 5 - Characterisation detail
+
+### prep
+
 ```{r}
@@
 # set the levels in that order
-test_by_attribute$marker2 <- factor(charact_by_marker_ref$marker2, 
+test_by_attribute$marker2 <- factor(test_by_attribute$marker2, 
                                     levels = test_cols)
-
+test_by_attribute$ref_number <- factor(test_by_attribute$ref_number, 
+                                    levels = c(levels(test_by_attribute$ref_number), "Total P", "Total M"))
 # status
@@
   mutate(test_status = recode_factor(status,
-                                     p = "Performed, value reported",
+                                     p = "Performed, value reported (by batch or average)",
                                      m = "Performed, no value reported",
-                                     n = "Not mentioned"))
+                                     n = "Not performed"))
 
 test_by_attribute$test_status <- fct_relevel(test_by_attribute$test_status,
+                                             "Not performed",
+                                             "Performed, no value reported",
+                                             "Performed, value reported (by batch or average)")
+test_by_attribute <- test_by_attribute %>% 
+  select(ref_number, marker2, test_status)
+
+# test_by_attribute$n <- 1
+
+# create the summary row & column
+# test_by_attribute_aug <- bind_rows(
+#   test_by_attribute,
+#   test_by_attribute %>% 
+#     filter(test_status == "Performed, value reported (by batch or average)") %>% 
+#     group_by(ref_number, .drop = FALSE) %>% 
+#     summarize(
+#       n = sum(n),
+#       marker2 = "Total P",
+#       test_status = "Performed, value reported (by batch or average)"
+  #   ),
+  # test_by_attribute %>% 
+  #   filter(test_status == "Performed, value reported (by batch or average)") %>% 
+  #   group_by(marker2, .drop = FALSE) %>% 
+  #   summarize(
+  #     n = sum(n),
+  #     ref_number = "Total P",
+  #     test_status = "Performed, value reported (by batch or average)"
+#     )
+# )
+# 
+# test_by_attribute_aug <- bind_rows(
+#   test_by_attribute_aug,
+#   test_by_attribute %>% 
+#     filter(test_status == "Performed, no value reported") %>% 
+#     group_by(ref_number, .drop = FALSE) %>% 
+#     summarize(
+#       n = sum(n),
+#       marker2 = "Total M",
+#       test_status = "Performed, no value reported"
+  #   ),
+  # test_by_attribute %>% 
+  #   filter(test_status == "Performed, no value reported") %>% 
+  #   group_by(marker2, .drop = FALSE) %>% 
+  #   summarize(
+  #     n = sum(n),
+  #     ref_number = "Total M",
+  #     test_status = "Performed, no value reported"
+#     )
+# )
+
+# test_by_attribute_aug$marker2 <- factor(test_by_attribute_aug$marker2, 
+#                                     levels = c(test_cols, "Total P", "Total M"))
+# test_by_attribute_aug$ref_number <- factor(test_by_attribute_aug$ref_number, 
+#                                     levels = levels(test_by_attribute$ref_number))
+
+test_by_attribute_summary <- test_by_attribute %>% 
+  group_by(marker2, test_status) %>% 
+  summarise(n = length(marker2))
+
+isct_pos <- c("CD73", "CD90", "CD105")
+isct_neg <- c("CD34", "CD45", "CD11b", "CD14", "CD79a", "CD19", "HLA-DR")
+isct_not <- c("viability",  "CD3" ,"CD13", "CD31", "CD133", "CD166", "CD29", "CD44", "CD146", "CD271", "STRO-1", "MSCA-1", "SSEA-4")
+
+test_by_attribute <- test_by_attribute %>%
+    mutate(ISCT = case_when(marker2 %in% isct_pos ~ "+",
+                            marker2 %in% isct_neg ~ "–",
+                            marker2 %in% isct_not ~ ""))
+test_by_attribute_summary <- test_by_attribute_summary %>%
+    mutate(ISCT = case_when(marker2 %in% isct_pos ~ "+",
+                            marker2 %in% isct_neg ~ "–",
+                            marker2 %in% isct_not ~ ""))
+codes <- data.frame(marker2 = test_cols)
+codes <- codes %>%
+  mutate(ISCT = case_when(marker2 %in% isct_pos ~ "+",
+                          marker2 %in% isct_neg ~ "–",
+                          marker2 %in% isct_not ~ ""))
+test_by_attribute$ref_number <- as.numeric(as.character(test_by_attribute$ref_number))
+```
+
+### each panel in figure 5
+
+```{r}
+
+# create the plot
+# fig5 <- test_by_attribute_aug %>% 
+#   ggplot() + 
+#   geom_tile(aes(x = marker2, y = ref_number, fill = test_status), colour = "white") + 
+#   scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
+#                     name = "Test results",
+#                     guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
+#   scale_x_discrete(name = "Characterisation attribute",
+#                      expand = c(0.02, 0)) +
+#   scale_y_discrete(expand = c(0, 0), name = "Reference") +
+#   geom_text(data = filter(test_by_attribute_aug, marker2 == 'Total P' | ref_number == 'Total P'| marker2 == 'Total M' | ref_number == 'Total M'), 
+#              aes(x = marker2, y = ref_number, label = n), size = 3, face = "bold") +
+#   theme_minimal() +
+#   theme(axis.text.x = element_text(size = 8, colour = "black",
+#                                    angle = 300, hjust = 0, vjust = 0.3),
+#         axis.text.y  = element_text(size = 8, colour = "black"),
+#         panel.grid.major.x = element_blank(),
+#         panel.grid.minor.x = element_blank(),
+#         panel.grid.minor.y = element_blank(),
+#         legend.position = "top",
+#         legend.text = element_text(size = 8, colour = "black"),
+#         legend.key.size = unit(0.2, "in"))
+
+# fig5 <- test_by_attribute_aug %>% 
+#   ggplot() + 
+#   geom_tile(aes(x = ref_number, y = marker2, fill = test_status), colour = "white") + 
+#   scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
+#                     name = "Test results",
+                    # guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
+#   scale_x_discrete(name = "Reference",
+#                      expand = c(0.02, 0)) +
+#   scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute" ) +
+#   geom_text(data = filter(test_by_attribute_aug, marker2 == 'Total P' | ref_number == 'Total P'| marker2 == 'Total M' | ref_number == 'Total M'), 
+#              aes(x = ref_number, y = marker2,  label = n), size = 3, face = "bold") +
+#   theme_minimal() +
+#   theme(axis.text.x = element_text(size = 8, colour = "black",
+#                                    angle = 300, hjust = 0, vjust = 0.3),
+#         axis.text.y  = element_text(size = 8, colour = "black"),
+#         panel.grid.major.x = element_blank(),
+#         panel.grid.minor.x = element_blank(),
+#         panel.grid.minor.y = element_blank(),
+#         legend.position = "top",
+#         legend.text = element_text(size = 8, colour = "black"),
+#         legend.key.size = unit(0.2, "in"))
+
+fig5a <- test_by_attribute %>% 
+  ggplot() + 
+  geom_tile(aes(x = ref_number, y = marker2, fill = test_status), colour = "white") + 
+  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
+                    name = "Test results",
+                    guide = guide_legend(nrow = 3)) +
+  scale_x_continuous(name = "Reference",
+                     breaks = seq(0, 84, 5),
+                     minor_breaks = seq(0, 84, 5),
+                     limits = c(1, 87),
+                     expand = c(0, 0)) +
+  scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute") +
+  # geom_text(aes(x = 85, y = marker2 , label = ISCT),
+  #           size = 2,
+  #           face = "bold") +
+  # coord_cartesian(xlim = c(0, 84), # This focuses the x-axis on the range of interest
+  #                 clip = 'off') +
+  theme_minimal() +
+  theme(axis.text.x = element_text(size = 8, colour = "black", hjust = 0.5,),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+         legend.position = "top",
+        legend.title = element_blank(),
+        legend.text = element_text(size = 8, colour = "black"),
+        legend.key.size = unit(0.1, "in"))
+
+fig5b <- test_by_attribute_summary %>% 
+  ggplot() +
+  geom_bar(aes(x = n, y = marker2, fill = test_status),
+           stat = "identity", width = 0.8, size = 0) +
+  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)])) +
+  scale_x_continuous(name = "Number of Articles",
+                     breaks = seq(0, 90, 10),
+                     minor_breaks = seq(0, 90, 10),
+                     limits = c(0, 85),
+                     expand = c(0, 0)) +
+  scale_y_discrete(expand = c(0, 0.5), name = NULL, labels = codes$ISCT) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 10, colour = "black",
+                                    face = "bold", vjust = 0.3),
+        axis.ticks.y = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.major.y = element_blank(),
+        legend.position = "none")
+
+```
+
+### the whole figure 5
+
+```{r}
+
+layout <- "
+aaab
+"
+
+fig5 <- fig5a +fig5b &
+  plot_layout(design = layout) &
+  plot_annotation(tag_levels = "A")&
+  geom_hline(yintercept = 1.5) &
+   geom_hline(yintercept = 11.5) &
+    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
+          plot.margin = margin(0,0,0,0))
+
+ggsave("figs/fig_5.svg", 
+       plot = fig5, 
+       device = device,
+       width = fig_w_2, 
+       height = fig_h * 1.2,
+       units = units)
+```
+
+## Fig 6 - functionality assessments
+
+### prep
+
+```{r}
+# panel a
+functionality <- dat %>% 
+  select(O, A, C, other) %>% 
+  pivot_longer(cols = everything(), names_to = "type", values_to = "status") %>% 
+  group_by(type, status) %>% 
+  summarise(n = length(status),
+            pc = paste0(round(100 * n / 84, 1 ), "%")) %>% 
+  ungroup(type, status)
+
+# status
+# relevel status
+functionality$status <- fct_relevel(functionality$status,
                                     "Not mentioned",
@@
 
-test_by_attribute_summary <- test_by_attribute %>% 
-  group_by(marker2, test_status) %>% 
-  summarise(n = length(marker2))
-
-```
-
-```{r}
-fig7 <- test_by_attribute_summary %>% 
-  ggplot() +
-  geom_bar(aes(x = marker2, y = n, fill = test_status),
-           stat = "identity", width = 0.6) +
-  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
-                    name = "Test results",
-                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
-  scale_y_continuous(name = "Number of Articles",
-                     breaks = seq(0, 90, 10),
-                     minor_breaks = seq(0, 90, 10),
-                     limits = c(0, 90),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0.5), name = "Characterisation attribute") +
-  geom_rect(xmin = 1.5, xmax = 11.5,
-            ymin = -Inf, ymax = Inf,
-            size = 1, linetype = 1, 
-            colour = "black", alpha = 0) +
-  labs(title = "Wilson, Alison, Figure 7. TOP" ) +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 6, colour = "black"),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        legend.position = "top",
-        legend.text = element_text(size = 8, colour = "black"),
-        legend.key.size = unit(0.2, "in")) +
-  coord_flip()
-
-ggsave("figs/fig_7_charact_by_marker.tif", 
-       plot = fig7, 
-       device = device,
-       width = fig_w_2, 
-       height = fig_h,
-       units = units,
-       dpi = dpi)
-
-```
-
-# Possible alternative to Fig 7 (and 6b)
-```{r}
-#alt fig
-fig7alt <- test_by_attribute %>% 
-  ggplot() +
-  geom_tile(aes(x = factor(ref_number), y = marker2 , fill = test_status),
-            colour = "white")+
-    scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
-                    name = "Test results",
-                    guide = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5 )) +
-  scale_x_discrete(name = "Reference",
-                     expand = c(0.01, 0)) +
-  scale_y_discrete(expand = c(0, 0), name = "Characterisation attribute") +
-  geom_rect(ymin = 1.5, ymax = 11.5,
-            xmin = -Inf, xmax = Inf,
-            size = 1, linetype = 1,
-            colour = "black", alpha = 0) +
-  labs(title = "Wilson, Alison, Figure 7ALT. TOP" ) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(size = 5, colour = "black", 
-                                   angle = 90, hjust = 0, vjust = 0.3),
-        axis.text.y  = element_text(size = 6, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        legend.position = "top",
-        legend.text = element_text(size = 8, colour = "black"),
-        legend.key.size = unit(0.2, "in"))
-
-ggsave("figs/fig_7_charact_by_marker_ALTERNATIVE.tif", 
-       plot = fig7alt, 
-       device = device,
-       width = fig_w_2, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-
-```
-
-# Figure 8
-```{r}
-functionality <- dat %>% 
-  select(O, A, C, other_functionality) %>% 
-  pivot_longer(cols = everything(), names_to = "type", values_to = "status") %>% 
-  group_by(type, status) %>% 
-  summarise(n = length(status)) %>% 
-  ungroup(type, status)
-
-# status
-# recode status
-functionality <- functionality %>%
-  mutate(status = recode_factor(status,
-                                p = "Performed",
-                                m = "Mentioned",
-                                n = "Not mentioned"))
-
-functionality$status <- fct_relevel(functionality$status,
-                                    "Not mentioned",
-                                    "Mentioned",
-                                    "Performed")
-levels(functionality$status)
-
 # recode functionality
@@
   mutate(type = recode_factor(type,
-                              other_functionality = "Other functionality",
+                              other = "Other functionality",
                               C = "Chondrogenesis",
@@
 
-```
-
-```{r}
-fig8 <- functionality %>% 
+# panel b
+moa_isct_summary <- dat %>% 
+  group_by(MOA, stem_stromal) %>% 
+  summarise(n = length(MOA),
+            pc = paste0(round(100 * n / 84, 1 ), "%"))
+
+# panel c
+diffmoasum <- dat %>% group_by(MOA, differentiation) %>% 
+  summarise(n = length(differentiation))
+```
+
+### each panel figure 6
+
+```{r}
+# panel a
+fig6a <- functionality %>% 
   ggplot() +
-  geom_bar(aes(x = type, y = n, fill = status),
-           stat = "identity", position = position_dodge()) +
-  scale_fill_manual(values =  c("#BABABA", pal[c(2, 5)]),
-                    name = "Assessment",
-                    guide = guide_legend(nrow = 2, title.position = "top", title.hjust = 0.5 )) +
+  geom_bar(aes(x = type, y = n, fill = status, label = pc),
+           stat = "identity") +
+  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
+                    name = " Functionality assessment",
+                    guide = guide_legend(nrow = 3, title.position = "top", title.hjust = 0.5 )) +
   scale_y_continuous(name = "Number of Articles",
@@
                      minor_breaks = seq(0, 80, 10),
-                     limits = c(0, 80),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0.5), name = "Functionality") +
-  labs(title = "Wilson, Alison, Figure 8. TOP" ) +
+                     limits = c(0, 85),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0.5), name = NULL) +
+  geom_text(data = filter(functionality, status == "Not mentioned"), aes(x = type, 50, label = pc) ) +
   theme_classic() +
@@
         panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
         legend.position = "top",
         legend.text = element_text(size = 8, colour = "black"),
-        legend.key.size = unit(0.2, "in")) +
+        legend.key.size = unit(0.1, "in")) +
   coord_flip()
 
-ggsave("figs/fig_8_functionality_assessment.tif", 
-       plot = fig8, 
-       device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-```
-
-# Figure 9
-
-## Relationship between MOA and stem/stromal
-
-```{r}
-moa_isct_summary <- dat %>% 
-  group_by(MOA, stem_stromal) %>% 
-  summarise(n = length(MOA))
-
-dat %>% 
-  group_by(stem_stromal) %>% 
-  summarise(n = length(stem_stromal),
-            pc = n/84)
-
-res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
-test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
-                   res$method, ": p = ", round(res$p.value, 3))
-
-```
-
-```{r moa-isct}
-moa_isct <- moa_isct_summary %>% 
+# panel b
+fig6b <- moa_isct_summary %>% 
   ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
@@
   scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 45, 5),
-                     minor_breaks = seq(0, 45, 5),
-                     limits = c(0, 45),
+                     breaks = seq(0, 40, 5),
+                     minor_breaks = seq(0, 40, 5),
+                     limits = c(0, 40),
                      expand = c(0, 0)) +
   scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
-  labs(title = "Wilson, Alison, Figure 9. TOP") +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black",
-                                   angle = -60, hjust = 0),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        plot.caption = element_text(size = 4, hjust = 0),
-        legend.position = c(0.7, 0.8),
-        legend.text = element_text(size = 6, colour = "black"),
-        legend.key.size = unit(0.2, "in"))
-ggsave("figs/fig_9_moa_isct.tif", 
-       plot = moa_isct, 
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        legend.position = "top",
+        legend.text = element_text(size = 8, colour = "black"),
+        legend.key.size = unit(0.1, "in")) +
+  coord_flip()
+
+# panel c
+fig6c <- diffmoasum %>%
+  ggplot(aes(x = MOA, y = n, fill = differentiation)) +
+  geom_bar(stat = "identity", size = 0) +
+   scale_fill_manual(values = c("#BABABA", pal[5]), 
+                    name = "Differentiation capacity",
+                    labels = c("Not demonstrated", "Demonstrated"),
+                    guide = guide_legend(nrow = 2, 
+                                         title.position = "top",
+                                         title.hjust = 0.5)) +
+  scale_y_continuous(name = "Number of Articles", 
+                     breaks = seq(0, 40, 5),
+                     minor_breaks = seq(0, 40, 5),
+                     limits = c(0, 40),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = NULL, labels =NULL) +
+  theme_classic() +
+  theme(axis.text.x = element_text(size = 8, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        legend.position = "top",
+        legend.text = element_text(size = 8, colour = "black"),
+        legend.key.size = unit(0.1, "in")) +
+  coord_flip()
+
+```
+
+### the whole figure 6
+
+```{r}
+
+layout <- "
+abc
+"
+
+fig6 <- fig6a + fig6b + fig6c +
+  plot_layout(design = layout) +
+  plot_annotation(tag_levels = "A")&
+    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
+ggsave("figs/fig_6.svg", 
+       plot = fig6, 
        device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
+       width = fig_w_2, 
+       height = 3,
+       units = units)
+
+```
+
+## Relationship between MOA and stem/stromal
+
+```{r}
+res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
+test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
+                   res$method, ": p = ", round(res$p.value, 3))
 
@@
 ## Figure 10 assocation between differentiation2 and MOA
-```{r}
-diffmoasum <- dat %>% group_by(MOA, differentiation_2) %>% 
-  summarise(n = length(differentiation_2))
-
-```
-
-```{r}
-moa_diff <- diffmoasum %>% 
-  ggplot(aes(x = MOA, y = n, fill = differentiation_2)) +
-  geom_bar(stat = "identity", size = 0) +
-   scale_fill_manual(values = pal[c(2,5)], 
-                    guide = guide_legend(nrow = 4, title = "Differentiation capacity"),
-                    labels = c("Not demonstrated", "Demonstrated")) +
-  scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 45, 5),
-                     minor_breaks = seq(0, 45, 5),
-                     limits = c(0, 45),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
-  labs(title = "Wilson, Alison, Figure 10. TOP") +
-  theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black",
-                                   angle = -60, hjust = 0),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.title = element_text(hjust = 0, size = 4),
-        plot.caption = element_text(size = 4, hjust = 0),
-        legend.position = c(0.7, 0.8),
-        legend.text = element_text(size = 6, colour = "black"),
-        legend.key.size = unit(0.2, "in"),
-        legend.title = element_text(size = 8))
-ggsave("figs/fig_10_moa_diff.tif", 
-       plot = moa_diff, 
-       device = device,
-       width = fig_w, 
-       height = fig_w,
-       units = units,
-       dpi = dpi)
-
-```
 
@@
 
-ggsave("figs/fig_x3_cd_refs_bar.tif", 
+ggsave("figs/fig_x3_cd_refs_bar.svg", 
        plot = cd_refs_bar, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x4_cd_values_isct.tif", 
+ggsave("figs/fig_x4_cd_values_isct.svg", 
        plot = cd_values_point_isct, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x5_cd_values_isct.tif", 
+ggsave("figs/fig_x5_cd_values_isct.svg", 
        plot = cd_values_point_other, 

### 2020-06-04 levels.R

@@ -1,10 +1,11 @@
+# TIDY
 # levelling factors
-dat$test_results_2 <- fct_relevel(dat$test_results_2,
-                                "Phenotypic markers reported (y)",
-                                "Average value (n)",
-                                "Tests done but not reported (t)",
-                                "Stated as 'standard phenotype' (s)",
-                                "Not discussed (o)")
+dat$test_results <- fct_relevel(dat$test_results,
+                                "1. % by batch reported",
+                                "2. Average % reported",
+                                "3. Tests done but % not reported",
+                                "4. Stated as 'standard phenotype'",
+                                "5. No characterisation discussed")
 dat$MOA <- fct_relevel(dat$MOA,
                        "Paracrine",
                        "Immune",
@@ -18,14 +19,27 @@ dat$stem_stromal <- fct_relevel(dat$stem_stromal,
                                 "Multipotent Stromal",
                                 "Regenerative")
 
-dat$funding <- fct_relevel(dat$funding,
-                           "Commercial",
-                           "National government",
-                           "Regional government",
-                           "Other grant",
-                           "Mix",
-                           "None",
-                           "Not stated")
+dat$O <- fct_relevel(dat$O,
+                     "Not mentioned",
+                     "Performed, no value reported",
+                     "Performed, value reported")
+
+dat$A <- fct_relevel(dat$A,
+                     "Not mentioned",
+                     "Performed, no value reported",
+                     "Performed, value reported")
+
+dat$C <- fct_relevel(dat$C,
+                     "Not mentioned",
+                     "Performed, no value reported",
+                     "Performed, value reported")
+dat$other <- fct_relevel(dat$other,
+                         "Not mentioned",
+                         "Performed, no value reported",
+                         "Performed, value reported")
 
 # turn year into a factor
 dat$year <- factor(dat$year)
+
+# turn ref in to a factor
+dat$ref_number <- factor(dat$ref_number) 

### 2020-06-04 scripts/working.R

@@ -1,40 +1,1 @@
-library(tidyverse)
-library(janitor)
 
-
-file <- "data/checked_processed_aw_corrections.csv"
-dat <- read_csv(file, skip = 1) 
-
-# note: 2019 values were made equal to 2018 values
-file <- "data/Human development index (HDI).csv"
-hdi <- read_csv(file) %>% clean_names() %>% select(-hdi_rank_2018)
-
-hdi <- hdi %>% 
-  pivot_longer(names_to = "year",
-               values_to = "index",
-               -country) %>% 
-  mutate(year = as.numeric(str_remove(year, "x"))) %>% 
-  filter(year > 2009) %>% 
-  filter(country %in% dat$country)
-
-
-length(unique(dat$country))
-length(unique(hdi$country))
-
-test <- merge(dat, hdi, by = c("country", "year"), all.x = TRUE)
-
-test[is.na(test$index), c("country","year")]
-
-file <- "data/test.csv"
-write_csv(test, file)
-
-
-data_dir <- "data/jif/"
-jif_files <- fs::dir_ls(data_dir)
-
-
-jif <- jif_files %>% 
-  map_dfr(read_csv)
-names(jif)[2] <- "journal"
-
-test <- merge(dat, jif, by = c("journal", "year"), all.x = TRUE)

### 2020-06-09 paper2.Rmd
transfer

---
title: 'Characterisation of MSC in clinical trial reports: analysis of published descriptors'
author: "Emma Rand"
date: "16/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r pkg}
library(tidyverse)
library(waffle)
library(RColorBrewer)
library(readxl)
library(kableExtra)
```

```{r}
blues <- brewer.pal(9,"Blues")
greens <- brewer.pal(9,"Greens")
excel_pal <- c("#CEDBE6", "#3494BA", "#58B6C0", "#75BDA7", "#84ACB6", "#2683C6", "#373545")
```

```{r import}
file <- here::here("data", "Meta-Analysis Data Collection.xlsx")

# added a row for column names more useful
# # skipped first two rows of of old col names

dat <- read_excel(file, sheet = "Data")

```

Note: there is a 85th line containing only a note in the `NOTES` variable - presumably it belongs elsewhere and was excluded. The note was "compares different papers on bone marrow MSCs, doesn't say anything about prep of cells"

```{r tidy-data}
# recode country so those with one paper are
# "Other"
dat <- dat %>%
  mutate(Country2 = recode_factor(Country,
                                Brazil = "Brazil",
                                China = "China",
                                Denmark = "Denmark",
                                Egypt = "Egypt",
                                India = "India",
                                Japan = "Japan",
                                Korea = "Korea",
                                Netherlands = "Netherlands",
                                Poland = "Poland",
                                `Rep Korea` = "Rep Korea",
                                Russia = "Russia",
                                Spain = "Spain",
                                Taiwan = "Taiwan",
                                USA = "USA",
                                .default = "Other"))

dat <- dat %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

# test results - there is no "t" in the data file and there are more
# blanks values than t's in draft paper fig 6
dat <- dat %>%
  mutate(test_results = recode_factor(`Test Results?`,
                                       n = "2. Average value",
                                       s = "4. Stated as 'standard phenotype'",
                                       o = "5. Not discussed",
                                       y = "1. Phenotypic markers reported",
                                       t = "3. Tests done but not reported"))
dat$test_results <- fct_relevel(dat$test_results,
                              "1. Phenotypic markers reported", 
                              "2. Average value",
                              "3. Tests done but not reported",
                              "4. Stated as 'standard phenotype'",
                              "5. Not discussed")

# dat <- dat %>%
#   mutate(Test.Results.2 = recode_factor(Test.Results.,
#                                        `Average value` = "Bulk values",
#                                        `Phenotypic markers reported` = "Phenotypic markers reported",
#                                        .default = "No characterisation data"))

######### code for "Data Tab copy v1.csv"
# # column indices for markers
# firstmarker <- which(colnames(dat) == "CD73")
# lastmarker <- which(colnames(dat) == "SSEA.4")
# # vector of marker names
# markers <- names(dat[firstmarker:lastmarker])
# 
# datnum <- dat %>% 
#   select(markers) %>% 
#   mutate_all(as.numeric) 
# 
# # add the non marker columns
# notmarkers <- which(!(colnames(dat) %in% markers))
# datnum <- cbind(dat[notmarkers], datnum)
# 
# 
# dat$Stem.Stromal <- factor(dat$Stem.Stromal)
# dat$Year <- factor(dat$Year)
# datnum$Stem.Stromal <- factor(datnum$Stem.Stromal)
# datnum$Year <- factor(datnum$Year)

```
# Some figures

Resolutions, colours, font types and size, labels, background colours and gridlines etc can be removed / adapted easily.

Once we've decided on figures, I'll turn them in to high res and big fonts suitable for shrinking.

## fig 1 - search terms

Funnel plot - could be adapted to include the reviews adjacent and aligned with the articles plot.

> to do: Add the Reviews diagram

```{r data-prep-fig1}
# create data
# short names for proof of method
orig <- data.frame(step_names = c("1.mesenchymal",
                                  "2.article",
                                  "3.cell tissue etc",
                                  "4.clinical etc",
                                  "5.not biotech etc",
                                  "6.exc conf etc"),
                   n = c(65706,
                         47031,
                         7814,
                         5502,
                         2055,
                         1986))

orig$step_names <- fct_relevel(orig$step_names,
                               "mesenchymal",
                               "article",
                               "cell tissue etc",
                               "clinical etc",
                               "not biotech etc",
                               "exc conf etc")

# prep polygons that connect
to_poly_orig <- orig %>%
  arrange(n) %>%
  mutate(
    group = row_number(),
    x1 = 0 + ((1 - n)/2),
    x4 = n + ((1 - n)/2),
    x2 = lag(x1), 
    x3 = lag(x4)) %>%
  mutate(
    x2 = ifelse(is.na(x2), x1, x2),
    x3 = ifelse(is.na(x3), x4, x3)
  ) %>%
  gather(xpoint, x, -step_names,-group, -n) %>%
  arrange(group, xpoint) %>%
  mutate(y = ifelse(xpoint %in% c("x2", "x3"), group, group + 1))

# EXAMPLE
# Create the placement of the stages in the plot,
#  by just adding a 0.5 to each row number

labels <- orig %>%
  arrange(n) %>%
  mutate(y = row_number() + 0.5)

# modify the labels
labels$step_names2 <- c( "EXCLUDE conference proceedings,\nretracted papers",
                         "EXCLUDE CATEGORIES (NOT\nbiotechnology applied microbiology oncology\nhaematology, engineering biomedical)",
                         "REFINE BY SOURCE TITLES\n(EXCLUDE NOT clinical/\ntranslation/regenerative medicine)",
                         "REFINE BY CATEGORY\ncell tissue engineering\nand transplantation",
                         "REFINE BY DOCUMENT TYPE\narticle",
                         "mesenchymal stem cells OR\nmesenchymal stromal cells OR\nMSC AND characterisation AND clinical")
```

```{r fig1}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               color = "grey10") +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 8,
            label.size = 0,
            label.padding = unit(0.2, "lines"),
            label.r = unit(0.2, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 20, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()) +
    scale_fill_manual(values = blues)

ggsave("figs/fig_1_Article_search_funnel_blues.png", 
       plot = article_funnel, 
       device = "png",
       width = 30, 
       height = 20,
       units = "cm")
```

## fig 3 papers by country

### bar
Better, With all the countries. Horizontal makes it easier to read Country names without rotating text.

```{r}
fig_3_Articles_by_country_blues <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4], color = "black") +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                    breaks = seq(0, 18, 1),
                    minor_breaks = seq(0, 18, 1),
                    limits = c(0, 18.5),
                    expand = c(0, 0)) +
  scale_x_discrete() +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text  = element_text(size = 20, colour = "black"),
        axis.title.x = element_text(size = 22)) +
  coord_flip()
ggsave("figs/fig_3_Articles_by_country_blues.png", 
       plot = fig_3_Articles_by_country_blues, 
       device = "png",
       width = 25, 
       height = 25,
       units = "cm") 
```

## fig 4 paper by phase

```{r waffle-phase-prep}
summary_phase <- dat %>%
  group_by(Phase) %>% 
  summarise(n = length(Phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))
summary_phase <- summary_phase %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III"))

summary_phase_condensed <- dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

```

Phase can comprise six or three categoires: `r unique(summary_phase$Phase)`; or three categories: `r unique(summary_phase_condensed$Phase_condensed)`

## waffle

### Six phase

```{r}
parts <- summary_phase$n
names(parts) <- summary_phase$Phase
waffle(parts,
       rows = 7,
       colors = blues[4:9])

```

### Three phase

```{r}
parts <- summary_phase_condensed$n
names(parts) <- summary_phase_condensed$Phase_condensed
waffle(parts,
       rows = 7,
       colors = blues[c(4, 6, 8)])

```

## Bar
as a bar. can add percentages as annotation if desired. can order bars as required.

### Six phase

```{r}
summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4]) +
  xlab("") +
  geom_text(aes(y = n / 2, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 30, 5),
                    minor_breaks = seq(0, 30, 1),
                    limits = c(0, 30),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.x = element_line(colour = "white", size = 0.3),
        panel.grid.major.y = element_blank(),
        axis.ticks = element_blank()) +
  coord_flip()
```

### Three phase

```{r}
summary_phase_condensed %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
  geom_bar(stat = "identity", fill = blues[4]) +
  xlab("") +
  geom_text(aes(y = n / 2, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 60, 10),
                    minor_breaks = seq(0, 60, 5),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.x = element_line(colour = "white", size = 0.3),
        panel.grid.major.y = element_blank(),
        axis.ticks = element_blank()) +
  coord_flip()
```

(will move percent if this figure is selected)

### Three and six phase both indicated
```{r}
summary_phase %>% 
  ggplot(aes(x = reorder(Phase_condensed, n), y = n, fill = Phase)) +
  geom_bar(stat = "identity", colour = "white") +
  xlab("") +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 60, 10),
                    minor_breaks = seq(0, 60, 5),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_manual(values = blues[4:9]) +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.x = element_line(colour = "white", size = 0.3),
        panel.grid.major.y = element_blank(),
        axis.ticks = element_blank()) +
  coord_flip()
```

## fig 5 paper msc source per year

```{r}
summary_tissue <- dat %>% 
  group_by(Year, Source) %>% 
  summarise(n = length(Source))

```

```{r}
summary_tissue %>% 
  ggplot(aes(x = factor(Year), y = n, fill = Source)) +
  geom_bar(stat = "identity", colour = "white") +
  scale_fill_manual(values = blues[4:9]) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 15, 1),
                    minor_breaks = seq(0, 15, 1),
                    limits = c(0, 15),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "") +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.y = element_line(colour = "white", size = 0.3),
        panel.grid.major.x = element_blank())
```

## fig 6

```{r}
summary_test <- dat %>% 
  group_by(test_results) %>% 
  summarise(n = length(test_results))

summary_test$x <- 1
tot <- sum(summary_test$n)
n <- summary_test$n
summary_test$lab_y <- c(n[1]/2,
                        n[1] + n[2]/2,
                        n[1] + n[2] + n[3]/2,
                        n[1] + n[2] + n[3] + n[4]/2,
                        n[1] + n[2] + n[3] + n[4] + n[5]/2)
```

Might you want test colours that indicate 'good' and 'bad' (green and grey maybe)
```{r}
summary_test %>% 
  ggplot(aes(x = x, y = n, fill = rev(test_results)) ) +
  geom_bar(stat = "identity", colour = "white", width = 0.5) +
  geom_text(aes(x = x, y = lab_y, label = n), size = 4) +
  geom_text(aes(x = 1.3, y = lab_y, label = test_results), hjust = 0 ) +
  scale_fill_manual(values = blues[3:7], name = "Test results") +
  scale_x_discrete(breaks = seq(0, 3, 1),
                   limits = c(0, 3)) +
    theme(panel.background = element_blank(),
          legend.position = "none",
          axis.title = element_blank(),
          axis.text = element_blank(), 
          axis.ticks = element_blank(),
          panel.grid.minor.y = element_line(colour = "white", size = 0.3),
          panel.grid.major.x = element_blank()) 
```

## figire 7 new phase and tests reported

### stacked by numbers
```{r}

summary_phase_test <- dat %>%
  group_by(Phase_condensed, test_results) %>% 
  summarise(n = length(Phase))
```
Might you want test colours that indicate 'good' and 'bad' (green and grey maybe)

```{r}
summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", colour = "white") +
  scale_fill_manual(values = blues[3:7], name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 55, 10),
                    minor_breaks = seq(0, 55, 5),
                    limits = c(0, 55),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.y = element_line(colour = "white", size = 0.3),
        panel.grid.major.x = element_blank())
```

### stacked by percent

```{r}
summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n)) +
  geom_bar(aes(fill = test_results), 
           stat = "identity", 
           colour = "white", 
           position = "fill") +
  scale_fill_manual(values = blues[3:7], name = "Test results") +
  scale_y_continuous(name = "Proportion of Articles by Phase",
                     breaks = seq(0, 1.1, 0.1),
                     # minor_breaks = seq(0, 1.1, 0.1),
                     # limits = c(0, 1.2),
                     expand = c(0, 0.1)) +
   scale_x_discrete(expand = c(0, 0), name = "Phase") +
    theme(panel.background = element_rect(fill = blues[2]),
                panel.grid = element_blank()) +
  geom_text(data = summary_phase_condensed, 
            aes(x = Phase_condensed, y = 1.05,
                label = paste("n = ",n)))
```

## Figure 9

There are some inconsistencies in the data file columns for markers (most have three associated columns (value, status and an unnamed one which appears to be a qualifier for the value and which I have named qualifier) but some have one a value but not status. It's not obv what the status should be in some cases.

The markers in this figure thus differ because I'm missed out the unknown status ones.

There's also a single "not stated" value remianing

```{r}
dat2 <- dat %>% 
  select(contains("_status")) %>% 
  rename_all(funs(stringr::str_replace(., fixed("_status"),"") )) %>% 
  gather(key = "marker", value = "status") %>%
  mutate(ISCT_pheno = recode_factor(marker,
                                CD73 = TRUE,
                                CD90 = TRUE,
                                CD105 = TRUE,
                                CD34 = TRUE,
                                CD45 = TRUE,
                                CD11b = TRUE,
                                CD14 = TRUE,
                                CD79a = TRUE,
                                CD19 = TRUE,
                                `HLA-DR` = TRUE,
                                .default = FALSE))  
# relevel the factor
dat2$marker <- fct_relevel(dat2$marker,
                           "viability", 
                           "CD73", 
                           "CD90", 
                           "CD105",
                           "CD34", 
                           "CD45", 
                           "CD11b",
                           "CD14", 
                           "CD79a",
                           "CD19",
                           "HLA-DR",
                           "CD133",
                           "CD166",
                           "CD29",
                           "CD44")
charc_marker <- dat2 %>%
  group_by(marker, status) %>% 
  summarise(n = length(marker))
charc_marker$marker <- fct_relevel(charc_marker$marker,
                           "viability", 
                           "CD73", 
                           "CD90", 
                           "CD105",
                           "CD34", 
                           "CD45", 
                           "CD11b",
                           "CD14", 
                           "CD79a",
                           "CD19",
                           "HLA-DR",
                           "CD133",
                           "CD166",
                           "CD29",
                           "CD44")
```

```{r}
charc_marker %>% 
  ggplot(aes(x = marker, y = n)) +
  geom_bar(aes(fill = status), 
           stat = "identity",
           position = "fill",
           colour = "white") +
  scale_fill_manual(values = blues[4:7], name = "Status") +
  scale_y_continuous(name = "Proportion of Articles") +
  scale_x_discrete(expand = c(0, 0), name = "Marker") +
  theme(panel.background = element_rect(fill = blues[2]),
        panel.grid = element_blank(),)

```

## Relationship between MOA and stem/stromal

```{r}
moa_isct_summary <- dat %>% 
  group_by(MOA, `Stem/Stromal`) %>% 
  summarise(n = length(MOA))

res <- table(dat$`Stem/Stromal`, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)

```

There is no significant association between MOA and cell categorisation (`r res$method`:  $p$ = `r res$p.value`).

```{r}
moa_isct_summary %>% 
  ggplot(aes(x = factor(MOA), y = n, fill = `Stem/Stromal`)) +
  geom_bar(stat = "identity", colour = "white") +
  scale_fill_manual(values = blues[5:8]) +
  scale_y_continuous(name = "Number of Articles", 
                    breaks = seq(0, 45, 5),
                    minor_breaks = seq(0, 45, 5),
                    limits = c(0, 45),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "MOA") +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.y = element_line(colour = "white", size = 0.3),
        panel.grid.major.x = element_blank())
```

## Relationship between types of differentiation (OAC) and MOA

There are five combinations for O, A and C potency. `y` is demonstrated, `m` is claimed but not demonstrated, `n` is not mentioned. These were recoded into a single variable, `potency` as follows:
```{r}
# there are five combinations of 
dat <- dat %>%
  mutate(potency = ifelse(O == "y" &
                            A == "y" &
                            C == "y",
                          "demonstrated tripotency",
                          ifelse(O == "n" &
                                   A == "n" &
                                   C == "n",
                                 "not mentioned",
                                 ifelse(O == "y" &
                                          A == "y" &
                                          C == "n",
                                        "demonstrated bipotency (OA)",
                                        ifelse(O == "m"
                                               & A == "m" &
                                                 C == "n",
                                               "claimed bipotency (OA)",
                                               ifelse(O == "m" &
                                                  A == "m" &
                                                  C == "m",
                                                  "claimed tripotency", NA))))))
```

```{r}
dat %>% 
  group_by(O, A, C, potency) %>% 
  summarise(n = length(O)) %>% 
  kable(format = "html") %>% 
  kable_styling()

```

```{r}
res <- table(dat$potency, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)

```

There is no significant association between MOA and cell categorisation (`r res$method`:  $p$ = `r res$p.value`).

```{r}
moa_potency_summary <- dat %>% 
  group_by(potency, MOA) %>% 
  summarise(n = length(MOA))
```

```{r}
moa_potency_summary %>% 
  ggplot(aes(x = factor(MOA), y = n, fill = potency)) +
  geom_bar(stat = "identity", colour = "white") +
  scale_fill_manual(values = blues[4:8]) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 45, 5),
                    minor_breaks = seq(0, 45, 5),
                    limits = c(0, 45),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "MOA") +
    theme(panel.background = element_rect(fill = blues[2]),
        panel.grid.minor.y = element_line(colour = "white", size = 0.3),
        panel.grid.major.x = element_blank())
```

## Claimed compliance vs categ compliance

```{r}
vals <- unique(dat$`ISCT compliance`)
ref <- dat$`Ref #`[is.na(dat$`ISCT compliance`)]
```

The values in `ISCT compliance` are: `r vals`
Probably the empty cell (formal NA in r) should be  "n/a" (a string). It's reference
`r ref`

```{r}

dat %>% 
  group_by(`ISCT compliance`,`ISCT claimed`) %>%
  summarise(n = length(`ISCT claimed`)) %>% 
  kable() %>% 
  kable_styling()

```
These results are so clear (all 14 of the papers that claim compliance do not demonstrate it; no other papers demonstrate it) that no further analysis is necessary.

## Relevance for indication, stem vs stromal
There are 50 different indications mostly with a single ref. This makes it difficult to deterimine if there is any relationalship between the nature of the ndication and whether treatment was with stem of stromal cells.

```{r}
dat %>% 
  group_by(Indication, `Stem/Stromal`) %>% 
  summarise(n = length(`Stem/Stromal`)) %>% 
  ggplot(aes(x = reorder(Indication, n), y = n, fill = `Stem/Stromal`)) +
  geom_col() +
  coord_flip()
```

```{r}
ind <- dat %>% 
  group_by(Indication) %>% 
  summarise(n = length(potency)) %>% 
  filter(n > 1)

dat %>% 
  group_by(Indication,potency) %>% 
  summarise(n = length(Indication)) %>% 
  filter(n > 1)
```

### 2020-06-28 paper2_figures.Rmd
updates to figures; removal of JIF and HDI data

@@
   ggplot(aes(x = reorder(country, n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[4],
+  geom_bar(stat = "identity", 
+           # fill = pal[4],
+           fill = "black",
            size = 0, width = 0.8) +
@@
   ggplot(aes(x = reorder(phase,n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity", 
+           # fill = pal[4],
+           fill = "black",
+           size = 0, 
+           width = 0.8) +
   xlab("") +
@@
   ggplot(aes(x = reorder(indication, n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity", 
+           # fill = pal[4], 
+           fill = "black", 
+           size = 0, 
+           width = 0.8) +
   xlab("") +
@@
   ggplot(aes(x = reorder(route, n), y = n)) +
-  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity", 
+           # fill = pal[4],
+            fill = "black",
+           size = 0, 
+           width = 0.8) +
   xlab("") +
@@
 bd
-bd
+cd
 cd
@@
 
-fig2 <- country_bar  + route_bar+ phase_bar+ indication_bar +
+fig2 <- country_bar + phase_bar + route_bar + indication_bar +
   plot_layout(design = layout) +
@@
 
-ggsave("figs/fig_2.svg", 
+ggsave("figs/fig_2_black.svg", 
        plot = fig2, 
@@
   ggplot(aes(x = source, y = n)) +
-  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity",
+           # fill = pal[4],
+           fill = "black",
+           size = 0, 
+           width = 0.8) +
   scale_y_continuous(name = "Number of Articles",
@@
   ggplot(aes(x = allo_auto, y = n)) +
-  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity",
+           # fill = pal[4], 
+           fill = "black",
+           size = 0, 
+           width = 0.8) +
   scale_y_continuous(name = NULL,
@@
   ggplot(aes(x = stem_stromal, y = n)) +
-  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
+  geom_bar(stat = "identity",
+           # fill = pal[4], 
+           fill = "black",
+           size = 0, 
+           width = 0.8) +
   scale_y_continuous(name = NULL,
@@
 
-ggsave("figs/fig_3.svg", 
+ggsave("figs/fig_3_black.svg", 
        plot = fig3, 
@@
                                     levels = test_cols)
-test_by_attribute$ref_number <- factor(test_by_attribute$ref_number, 
-                                    levels = c(levels(test_by_attribute$ref_number), "Total P", "Total M"))
+test_by_attribute$ref_number <- factor(test_by_attribute$ref_number)
 # status
@@
 
+moa_isct_summary$stem_stromal <- fct_relevel(moa_isct_summary$stem_stromal,
+                                         "Stem",
+                                         "Stromal",
+                                         "Multipotent Stromal",
+                                         "Regenerative")
+
+moa_isct_summary$MOA <- fct_relevel(moa_isct_summary$MOA,
+                                    "Not stated",
+                                    "Multiple",
+                                    "Differentiation",
+                                    "Immune",
+                                    "Paracrine")
+
 # panel c
@@
   summarise(n = length(differentiation))
+
+diffmoasum$MOA <- fct_relevel(diffmoasum$MOA,
+                                     "Not stated",
+                                    "Multiple",
+                                    "Differentiation",
+                                    "Immune",
+                                    "Paracrine")
+
+diffmoasum$differentiation <- fct_relevel(diffmoasum$differentiation,
+                                          "No",
+                                          "Yes")
+
 ```
@@
   geom_bar(aes(x = type, y = n, fill = status, label = pc),
-           stat = "identity") +
+           stat = "identity", size = 0) +
   scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
-                    name = " Functionality assessment",
-                    guide = guide_legend(nrow = 3, title.position = "top", title.hjust = 0.5 )) +
+                    name = " Functionality",
+                    guide = guide_legend(nrow = 4,
+                                         title.position = "top",
+                                         title.hjust = 0 )) +
   scale_y_continuous(name = "Number of Articles",
@@
   scale_x_discrete(expand = c(0, 0.5), name = NULL) +
-  geom_text(data = filter(functionality, status == "Not mentioned"), aes(x = type, 50, label = pc) ) +
+  geom_text(data = filter(functionality, 
+                          status == "Not mentioned"),
+            aes(x = type, 50, label = pc) ) +
   theme_classic() +
@@
         axis.text.y  = element_text(size = 8, colour = "black"),
+        plot.margin = margin(t = 0, r = 30),
         panel.grid.major.x = element_blank(),
@@
   scale_fill_manual(values = pal, 
-                    guide = guide_legend(nrow = 4, title = NULL)) +
+                    name = "Nomenclature",
+                    guide = guide_legend(nrow = 4,
+                                         title.position = "top",
+                                         title.hjust = 0 )) +
   scale_y_continuous(name = "Number of Articles", 
@@
                      minor_breaks = seq(0, 40, 5),
-                     limits = c(0, 40),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
+                     limits = c(0, 42),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = "MOA") +
   theme_classic() +
@@
         axis.text.y  = element_text(size = 8, colour = "black"),
+        plot.margin = margin(t = 0, r = 0, l = 0),
         panel.grid.major.x = element_blank(),
@@
                     labels = c("Not demonstrated", "Demonstrated"),
-                    guide = guide_legend(nrow = 2, 
+                    guide = guide_legend(nrow = 4, 
                                          title.position = "top",
-                                         title.hjust = 0.5)) +
+                                         title.hjust = 0)) +
   scale_y_continuous(name = "Number of Articles", 
@@
                      minor_breaks = seq(0, 40, 5),
-                     limits = c(0, 40),
+                     limits = c(0, 42),
                      expand = c(0, 0)) +
@@
 ```{r}
-res <- table(dat$stem_stromal, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
+res <- table(dat$stem_stromal, dat$MOA) %>%
+  fisher.test(simulate.p.value = TRUE)
 test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",

### 2020-07-01 paper2_figures.Rmd
figs amended, wmf added, list of figs added

@@
 # Figures specification
-* titled
-* cited in numerical order in the text using Arabic numbers. 
-* no additional charges for color. 
-* submitted as individual files
-* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
-* Figures may be submitted as multipart panels.
-*  *.svg* or .eps 
-* final publication size; 1-column width or, if necessary, 1½ column width. The  2-column width should not be used unless necessary.
-* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
-* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
-* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
-* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
-* Calibri font sub sans serif Arial
-* Multipanel labeled using uppercase 12-point Calibri Bold. 
-* minimum text size of 6 points
-* bold enough to be easily read after reduction, as should all symbols used in the * figure.
-Line or bar graphs or flow charts with text should be created in black and white, not shades of gray, which are difficult to reproduce in even tones.
-If more than two sets of data are represented, use of fill patterns or colors (not gray) is suggested to present the data clearly.
-* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for  combination halftones, and 1000 dpi for line art.
+Vector-based files 
+150 to 300 dots per inch (dpi) for initial submission. A higher resolution applies for figures submitted at the revision stage.
+
+Fit on single 8.5" × 11" or A4 paper
+Preferably at:
+1 column - 3.5 inches
+1.5 columns - 5.0 inches
+2 columns = 7.3 inches
+
+The figure title should be at the beginning of the figure legend
+Include the fig id on same page that includes the figure
 
@@
 units = "in"
-fig_w <- 3.5
-fig_w_1.5 <- 5
-fig_w_2 <- 7.3
+fig_w <- 3.5 # one col
+fig_w_1.5 <- 5 # 1.5 col
+fig_w_2 <- 7.3 # 2 col
 fig_h <- fig_w
-device <- "svg"
 
@@
        plot = fig1, 
-       device = device,
+       device = "svg",
        width = fig_w, 
@@
        plot = fig2, 
-       device = device,
+       device = "svg",
        width = fig_w_2, 
@@
        plot = fig3, 
-       device = device,
+       device = "svg",
        width = fig_w_1.5, 
@@
   ggplot(aes(x = marker_p_count, y = n)) +
-  geom_bar(stat = "identity", fill = pal[6], size = 0, width = 0.8) +
+  geom_bar(stat = "identity", fill = "black", size = 0, width = 0.8) +
   scale_y_continuous(name = NULL, 
@@
         panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank())
+        panel.grid.minor.y = element_blank(),
+        plot.margin = margin(t = 0, r = 0, l = 0))
 
@@
        plot = fig4, 
-       device = device,
+       device = "svg",
        width = fig_w_2, 
@@
        plot = fig5, 
-       device = device,
+       device = "svg",
        width = fig_w_2, 
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A")&
+  plot_annotation(tag_levels = "A") &
     theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
@@
        plot = fig6, 
-       device = device,
+       device = "svg",
        width = fig_w_2, 
@@
        plot = cd_refs_bar, 
-       device = device,
+       device = "svg",
        width = fig_w, 
@@
        plot = cd_values_point_isct, 
-       device = device,
+       device = "svg",
        width = fig_w_1.5, 
@@
        plot = cd_values_point_other, 
-       device = device,
+       device = "svg",
        width = fig_w_1.5, 

### 2020-07-07 sticker.R
update journal urls; create hex

@@ -1,0 +1,22 @@
+library(hexSticker)
+library(tidyverse)
+library(png)
+library(grid)
+library(ggimage)
+img <- "image.png"
+
+# border 95AAD3
+# 
+
+
+sticker(img, package = "MSC-CT",
+        p_size=25, 
+        p_x = 1,
+        p_y = 1.5,
+        p_color = "#22A884",
+        h_fill = "white",
+        h_color = "#440154",
+        s_x = 1, s_y = 0.8,
+        asp = 0.85,
+        s_width = .6,
+        filename="hex.png")

### 2020-08-10 paper2_figures.Rmd
fig updates for data update

@@
   html_document: default
-  svg_document: default
+  wmf_document: default
 ---
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A")&
+  plot_annotation(tag_levels = "A") &
     theme(plot.tag = element_text(size = 9, hjust = 1, face = "bold"))
 
-ggsave("figs/fig_1.svg", 
+ggsave("figs/fig_1.wmf", 
        plot = fig1, 
-       device = "svg",
+       device = "wmf",
        width = fig_w, 
@@
   scale_y_continuous(name = NULL, 
-                     breaks = seq(0, 35, 10),
-                     minor_breaks = seq(0, 35, 1),
-                     limits = c(0, 35),
+                     breaks = seq(0, 20, 10),
+                     minor_breaks = seq(0, 20, 1),
+                     limits = c(0, 25),
                      expand = c(0, 0)) +
@@
 
-ggsave("figs/fig_2_black.svg", 
+ggsave("figs/fig_2_black.wmf", 
        plot = fig2, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_2, 
@@
 
-fig3 <- source_bar  + allo_auto_bar+ stem_stromal_bar +
+fig3 <- source_bar  + allo_auto_bar + stem_stromal_bar +
   plot_layout(design = layout) +
   plot_annotation(caption = "Source",
-                  tag_levels = "A")&
+                  tag_levels = "A") &
     theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
@@
 
-ggsave("figs/fig_3_black.svg", 
+ggsave("figs/fig_3_black.wmf", 
        plot = fig3, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_1.5, 
@@
 ```{r fig_4-layout}
-layout <- "
-#aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa
-bbbcccccccccccccccccccccccccccccccccccc
-"
 
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A")&
+  plot_annotation(tag_levels = "A") &
     theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
 
-ggsave("figs/fig_4.svg", 
+ggsave("figs/fig_4.wmf", 
        plot = fig4, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_2, 
@@
 
-fig5 <- fig5a +fig5b &
+fig5 <- fig5a + fig5b &
   plot_layout(design = layout) &
-  plot_annotation(tag_levels = "A")&
+  plot_annotation(tag_levels = "A") &
   geom_hline(yintercept = 1.5) &
@@
 
-ggsave("figs/fig_5.svg", 
+ggsave("figs/fig_5.wmf", 
        plot = fig5, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_2, 
@@
   scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 40, 5),
-                     minor_breaks = seq(0, 40, 5),
-                     limits = c(0, 42),
+                     breaks = seq(0, 30, 5),
+                     minor_breaks = seq(0, 30, 5),
+                     limits = c(0, 35),
                      expand = c(0, 0)) +
@@
   scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 40, 5),
-                     minor_breaks = seq(0, 40, 5),
-                     limits = c(0, 42),
-                     expand = c(0, 0)) +
-  scale_x_discrete(expand = c(0, 0), name = NULL, labels =NULL) +
+                     breaks = seq(0, 30, 5),
+                     minor_breaks = seq(0, 30, 5),
+                     limits = c(0, 35),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0), name = NULL, labels = NULL) +
   theme_classic() +
@@
     theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
-ggsave("figs/fig_6.svg", 
+ggsave("figs/fig_6.wmf", 
        plot = fig6, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_2, 
@@
        units = units)
+
+```
+
+## relationship between phase_condensed and test_results
+
+```{r}
+res <- table(dat$phase_condensed, dat$test_results) %>%
+  fisher.test(simulate.p.value = TRUE)
+test_anno <- paste0("There is no significant association between MOA and cell categorisation\n(",
+                   res$method, ": p = ", round(res$p.value, 3))
 
@@
 
-```
-
-## Figure 10 assocation between differentiation2 and MOA
-
-```{r}
-res <- table(dat$differentiation_2, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
-chisq.test(table(dat$differentiation_2, dat$MOA))$exp;table(dat$differentiation_2, dat$MOA)
-test_anno <- paste0("There is  significant association between MOA and demonstration of differentiation capacity(", res$method, ": p = ", round(res$p.value, 3),") with more studies demonstrating differentiation for Immune MOA, and fewer for Paracrine and Multiple MOA than expected.")
+# without the regen and multi cats
+dat_sub <- dat %>%
+  filter(stem_stromal != "Regenerative") %>% 
+  filter(stem_stromal != "Multipotent Stromal") %>% droplevels()
+res <- table(dat_sub$stem_stromal, dat_sub$MOA) %>% 
+  fisher.test(simulate.p.value = TRUE)
+
+```
+
+## Figure 10 assocation between differentiation and MOA
+
+```{r}
+res <- table(dat$differentiation, dat$MOA) %>% fisher.test(simulate.p.value = TRUE)
+
 ```
@@
 
-ggsave("figs/fig_x3_cd_refs_bar.svg", 
+ggsave("figs/fig_x3_cd_refs_bar.wmf", 
        plot = cd_refs_bar, 
-       device = "svg",
+       device = "wmf",
        width = fig_w, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x4_cd_values_isct.svg", 
+ggsave("figs/fig_x4_cd_values_isct.wmf", 
        plot = cd_values_point_isct, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_1.5, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x5_cd_values_isct.svg", 
+ggsave("figs/fig_x5_cd_values_isct.wmf", 
        plot = cd_values_point_other, 
-       device = "svg",
+       device = "wmf",
        width = fig_w_1.5, 

### 2020-08-10 scripts/emma.R

@@ -1,135 +1,0 @@
-# Emma - analysis
-# packaes needed
-library(tidyverse)
-
-# this sets your working directory to the location of emma.R
-# all the other file paths are given relative to this script
-here::here()
-
-
-# import
-# character values will be read as character datatypes rather than factors
-# which makes processing easier in the first instance
-# note: last record contained no info except: 
-#     "compares different papers on bone marrow MSCs, 
-#     doesn't say anything about prep of cells"
-#   This was deleted (perhaps it belongs on another line?)
-
-dat <- read.csv("../data/Data Tab copy v1.csv", stringsAsFactors = FALSE)
-
-# column indices for markers
-firstmarker <- which(colnames(dat) == "CD73")
-lastmarker <- which(colnames(dat) == "SSEA.4")
-# vector of marker names
-markers <- names(dat[firstmarker:lastmarker])
-
-datnum <- dat %>% 
-  select(markers) %>% 
-  mutate_all(list(num = ~ as.numeric(.))) 
-
-# do the same for binary coding: 0 or 1
-
-dat <- cbind(dat, datnum[,24:46])
-dat$Stem.Stromal <- factor(dat$Stem.Stromal)
-dat$Year <- factor(dat$Year)
-
-# stacked - my preference
-ggplot(data = dat, aes(x = Year, fill = Stem.Stromal)) +
-  geom_bar(colour = "black") +
-  theme_classic() +
-  ylab("Frequency") +
-  xlab("Year")
-
-              
-# besides data summary
-datsum <- dat %>% 
-  group_by(Stem.Stromal, Year, .drop = FALSE) %>% 
-  summarise(n = length(Ref..))
-  
-# besides
-ggplot(data = datsum, aes(x = Year, y = n, fill = Stem.Stromal)) +
-  geom_bar(stat = "identity", position = position_dodge()) +
-  theme_classic() +
-  ylab("Frequency") +
-  xlab("Year")
-
-table(dat$Phase)
-ggplot(data = dat, aes(x = Phase, fill = Stem.Stromal)) +
-  geom_bar(colour = "black") +
-  theme_classic() +
-  ylab("Frequency") +
-  xlab("Phase")
-
-datnum2 <- datnum %>% 
-  select(ends_with("_num")) %>% 
-  gather(key = marker, value = value)
[…]

### 2020-08-10 scripts/working.R

@@ -1,2 +1,89 @@
 
 # empty
+
+route_bar <- summary_route %>% 
+  ggplot(aes(x = reorder(route, n), y = n)) +
+  geom_bar(stat = "identity", 
+           # fill = pal[4],
+           fill = "black",
+           size = 0, 
+           width = 0.8) +
+  xlab("") +
+  #  geom_text(aes(y = n + 3, label = pc) ) +
+  scale_y_continuous(name = NULL, 
+                     breaks = seq(0, 25, 5),
+                     minor_breaks = seq(0, 25, 1),
+                     limits = c(0, 25),
+                     expand = c(0, 0)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.text.x = element_text(size = 8, colour = "black"),
+        axis.ticks.y = element_blank(),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.title = element_text(hjust = 0, size = 4))
+
+
+
+library(showtext)
+## Loading Google fonts (https://fonts.google.com/)
+font_add_google("Gochi Hand", "gochi")
+font_add_google("Schoolbell", "bell")
+font_add_google("Schoolbell", "Schoolbell")
+font_add_google("Coming Soon", "Coming Soon")
+font_add_google("Architects Daughter", "Architects Daughter")
+font_add_google("Pangolin")
+
+## Automatically use showtext to render text
+showtext_auto()
+p <- route_bar +
+  annotate("text", 
+           x = 4, 
+           y = 10, 
+           label = "Gochi Hand", 
+           family = "gochi", 
+           size = 10, 
+           colour = "#f88f88") +
+  geom_curve(aes(x = 3.5, 
+                 xend = 4.5, 
+                 y = 8, 
+                 yend = 4), 
+             curvature = 0.4, 
+             size = 2,
+             arrow = arrow(length = unit(0.0175, "npc")),
+             colour = "#6eb4e9") +
+  annotate("text", 
+           x = 6, 
+           y = 12, 
+           label = "Schoolbell", 
+           family = "Schoolbell", 
+           size = 10, 
+           colour = "#f88f88") +
+  annotate("text", 
+           x = 8, 
+           y = 15, 
+           label = "Coming Soon", 
[…]

### 2020-08-10 sticker.R

@@ -8,15 +8,20 @@ img <- "image.png"
 # border 95AAD3
 # 
 
-
-sticker(img, package = "MSC-CT",
-        p_size=25, 
+apname <- "CIDMap"
+sticker(img, package = apname,
+        p_size = 20, 
         p_x = 1,
-        p_y = 1.5,
+        p_y = 1.55,
         p_color = "#22A884",
         h_fill = "white",
         h_color = "#440154",
-        s_x = 1, s_y = 0.8,
+        s_x = 1, s_y = 0.9,
         asp = 0.85,
         s_width = .6,
-        filename="hex.png")
+        filename = "hex.png",
+        url = "https://shiny.york.ac.uk/er13/CIDMap",
+        u_color = "#22A884",
+        u_size = 4.5,
+        u_y = 0.080,
+        u_x = 0.97)

### 2020-09-04 paper2_figures.Rmd
fig updates
fig formatting for SCTM

@@
   html_document: default
-  wmf_document: default
+  tiff_document: default
 ---
@@
 
-Fit on single 8.5" × 11" or A4 paper
+fig size for SCTM
+height no more than 9.6 inches
 Preferably at:
-1 column - 3.5 inches
-1.5 columns - 5.0 inches
-2 columns = 7.3 inches
+1 column - 3.2 inches
+1.5 columns - 4.5 inches
+2 columns = 5.8 inches
 
@@
 library(janitor)
-
-```
-
-```{r}
-
+library(showtext)
+
+```
+
+```{r}
+#showtext_auto()
+conv <- 0.352778
 # palette
@@
 units = "in"
-fig_w <- 3.5 # one col
-fig_w_1.5 <- 5 # 1.5 col
-fig_w_2 <- 7.3 # 2 col
+fig_w <- 3.2 # one col
+fig_w_1.5 <- 4.5 # 1.5 col
+fig_w_2 <- 5.8 # 2 col
 fig_h <- fig_w
@@
   theme_minimal() +
-  theme(legend.position = "none",
+  theme(text = element_text(family = "Calibri", size = 8),
+        legend.position = "none",
         axis.title = element_blank(),
@@
         axis.ticks.x = element_blank(),
-        axis.text.y  = element_text(size = 7, colour = "black", hjust = 0, face = "plain"),
+        axis.text.y  = element_text(colour = "black", hjust = 0, face = "plain"),
         panel.spacing = unit(0, "lines"),
@@
   theme_minimal() +
-  theme(legend.position = "none",
-        strip.text = element_text(hjust = 0, size = 5.5, colour = "white", face = "bold"),
+  theme(text = element_text(family = "Calibri", size = 10),
+        legend.position = "none",
+        strip.text = element_text(size = 8, hjust = 0, colour = "white", face = "bold"),
         strip.background = element_rect(fill = pal[1], colour = pal[1], size = 0.05),
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A") &
-    theme(plot.tag = element_text(size = 9, hjust = 1, face = "bold"))
-
-ggsave("figs/fig_1.wmf", 
+  plot_annotation(tag_levels = "A",
+                  title = "Wilson, Alison, Figure 1. TOP") &
+    theme(plot.tag = element_text(size = 12,
+                                  hjust = 1,
+                                  face = "bold",
+                                  family = "Calibri"),
+        plot.title = element_text(size = 6))
+
+ggsave("figs/fig_1.tiff", 
        plot = fig1, 
-       device = "wmf",
-       width = fig_w, 
-       height = fig_h*1.6,
+       device = "tiff",
+       width = fig_w_1.5, 
+       height = fig_h*1.8,
        units = units)
@@
   theme_classic() +
-  theme(axis.title.y = element_blank(),
+  theme(text = element_text(family = "Calibri"),
+        axis.title.y = element_blank(),
         axis.text.x = element_text(size = 8, colour = "black"),
@@
   plot_annotation(caption = "Number of Articles",
-                  tag_levels = "A")&
-    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
-          plot.caption = element_text(size = 9, hjust = 0.5, face = "plain"))
-
-ggsave("figs/fig_2_black.wmf", 
+                  tag_levels = "A",
+                  title = "Wilson, Alison, Figure 2. TOP") &
+    theme(plot.tag = element_text(size = 12,
+                                  hjust = 1,
+                                  face = "bold",
+                                  family = "Calibri"),
+         plot.title = element_text(size = 6),
+         plot.caption.position = "plot",
+         plot.caption = element_text(hjust = 0.5, size = 12))
+
+ggsave("figs/fig_2_black.tiff", 
        plot = fig2, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_2, 
-       height = fig_h*2,
+       height = fig_h*2.2,
        units = units)
@@
            width = 0.8) +
-  scale_y_continuous(name = "Number of Articles",
+  scale_y_continuous(name = "No. Articles",
                     breaks = seq(0, 50, 10),
@@
   plot_annotation(caption = "Source",
-                  tag_levels = "A") &
-    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
-          plot.caption = element_text(size = 9, hjust = 0.5, vjust = 1, face = "plain"))
-
-ggsave("figs/fig_3_black.wmf", 
+                  tag_levels = "A",
+                  title = "Wilson, Alison, Figure 3. TOP") &
+    theme(plot.tag = element_text(size = 12, 
+                                  hjust = 0, 
+                                  face = "bold",
+                                  family = "Calibri"),
+          plot.title = element_text(size = 6),
+          plot.caption = element_text(size = 12, 
+                                      hjust = 0.5, 
+                                      vjust = 1, 
+                                      family = "Calibri"))
+
+ggsave("figs/fig_3_black.tiff", 
        plot = fig3, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_1.5, 
@@
   xlab("") +
-  geom_text(aes(y = n + 6, label = pc), size = 3 ) +
+  geom_text(aes(y = n + 7, label = pc), size = 2.5 ) +
   scale_fill_manual(values = rev(pal[1:5]),
                     name = "Test results") +
-  scale_y_continuous(name = "Number of Articles", 
-                     breaks = seq(0, 50, 5),
+  scale_y_continuous(name = "No. Articles", 
+                     breaks = seq(0, 50, 10),
                      minor_breaks = seq(0, 50, 1),
-                     limits = c(0, 53),
+                     limits = c(0, 55),
                      expand = c(0, 0)) +
@@
         axis.text.y  = element_text(size = 8, colour = "black"),
-        plot.margin = margin(t = 0, r = 30),
+        plot.margin = margin(t = 0, r = 20, l = 0),
         panel.grid.major.x = element_blank(),
@@
                     name = NULL) +
-  scale_y_continuous(name = "Number of Articles",
+  scale_y_continuous(name = "No. Articles",
                      breaks = seq(0, 55, 10),
@@
                      expand = c(0, 0)) +
-  scale_x_continuous(name = "Number of markers",
+  scale_x_continuous(name = "No. markers",
                      breaks = seq(0, 11, 1),
@@
   theme_classic() +
-  theme(axis.text.x = element_text(size = 8, colour = "black"),
-        axis.text.y  = element_text(size = 8, colour = "black"),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        panel.grid.minor.y = element_blank(),
-        plot.margin = margin(t = 0, r = 0, l = 0))
+  theme(axis.text.x = element_text(size = 6, colour = "black"),
+        axis.text.y  = element_text(size = 8, colour = "black"),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        plot.margin = margin(t = 0, r = 1, l = 0))
 
@@
 layout <- "
-aaaaaabbbcccc
+aaaaaabbbccccc
 "
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A") &
-    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
-
-ggsave("figs/fig_4.wmf", 
+  plot_annotation(tag_levels = "A",
+                  title = "Wilson, Alison, Figure 4. TOP") &
+    theme(plot.tag = element_text(size = 12,
+                                  hjust = 1,
+                                  face = "bold",
+                                  family = "Calibri"),
+         plot.title = element_text(size = 6))
+
+ggsave("figs/fig_4.tiff", 
        plot = fig4, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_2, 
@@
   scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)])) +
-  scale_x_continuous(name = "Number of Articles",
+  scale_x_continuous(name = "No. Articles",
                      breaks = seq(0, 90, 10),
@@
   plot_layout(design = layout) &
-  plot_annotation(tag_levels = "A") &
+  plot_annotation(tag_levels = "A",
+                  title = "Wilson, Alison, Figure 5. TOP") &
   geom_hline(yintercept = 1.5) &
    geom_hline(yintercept = 11.5) &
-    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
+    theme(plot.tag = element_text(size = 12, 
+                                  hjust = 0,
+                                  face = "bold",
+                                  family = "Calibri"),
+          plot.title = element_text(size = 6),
           plot.margin = margin(0,0,0,0))
 
-ggsave("figs/fig_5.wmf", 
+ggsave("figs/fig_5.tiff", 
        plot = fig5, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_2, 
@@
                                          title.hjust = 0 )) +
-  scale_y_continuous(name = "Number of Articles",
-                     breaks = seq(0, 80, 10),
+  scale_y_continuous(name = "No. Articles",
+                     breaks = seq(0, 80, 20),
                      minor_breaks = seq(0, 80, 10),
@@
         axis.text.y  = element_text(size = 8, colour = "black"),
+        axis.title = element_text(size = 8, colour = "black"),
         plot.margin = margin(t = 0, r = 30),
@@
         legend.text = element_text(size = 8, colour = "black"),
+        legend.title = element_text(size = 8, colour = "black"),
         legend.key.size = unit(0.1, "in")) +
@@
                                          title.hjust = 0 )) +
-  scale_y_continuous(name = "Number of Articles", 
+  scale_y_continuous(name = "No. Articles", 
                      breaks = seq(0, 30, 5),
@@
         axis.text.y  = element_text(size = 8, colour = "black"),
+        axis.title = element_text(size = 8, colour = "black"),
         plot.margin = margin(t = 0, r = 0, l = 0),
@@
                                          title.hjust = 0)) +
-  scale_y_continuous(name = "Number of Articles", 
+  scale_y_continuous(name = "No. Articles", 
                      breaks = seq(0, 30, 5),
@@
   plot_layout(design = layout) +
-  plot_annotation(tag_levels = "A") &
-    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"))
-ggsave("figs/fig_6.wmf", 
+  plot_annotation(tag_levels = "A",
+                  title = "Wilson, Alison, Figure 6. TOP") &
+    theme(plot.tag = element_text(size = 12,
+                                  hjust = 0,
+                                  face = "bold",
+                                  family = "Calibri"),
+          title = element_text(size = 6))
+
+ggsave("figs/fig_6.tiff", 
        plot = fig6, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_2, 
@@
 
-ggsave("figs/fig_x3_cd_refs_bar.wmf", 
+ggsave("figs/fig_x3_cd_refs_bar.tiff", 
        plot = cd_refs_bar, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x4_cd_values_isct.wmf", 
+ggsave("figs/fig_x4_cd_values_isct.tiff", 
        plot = cd_values_point_isct, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_1.5, 
@@
         plot.title = element_text(hjust = 0, size = 4))
-ggsave("figs/fig_x5_cd_values_isct.wmf", 
+ggsave("figs/fig_x5_cd_values_isct.tiff", 
        plot = cd_values_point_other, 
-       device = "wmf",
+       device = "tiff",
        width = fig_w_1.5, 
